---
title: "A2_ChecklistChile"
author: "Johanna Klapper"
date: "3/4/2022"
output: html_document
---

For Chile/Atacama we have to remove the doublets, filter out the non-native species, merge the list with the large checklist file based on species names and finally filter for those species which are distributed below 3000 m.
     

# Load packages
```{r}
library(tidyverse)
```

# Load data
```{r}
chile_csv <- read.csv(here::here("data/20220301_Zuloaga_Atacama_Antofagasta_Tarapaca.csv"), sep = ";")
chile_rds <- readRDS(here::here("./data/20220301_Zuloaga_range.rds"))
```

# Inspect data
```{r}
str(chile_rds)
str(chile_csv)
```


# Species selection

## Non-native species + doublets

```{r}
chile_uni <- chile_csv %>% 
  filter(native == 1) %>% 
  distinct(species, .keep_all = TRUE)
```

## Join .csv with range file (.rds)
```{r}
chile_joined <- full_join(chile_uni, chile_rds, by = "species")
chile_joined %>% 
  filter(is.na(ref_ID.y)) # 166 species from .csv which are not in range rds
```

## Double entries
```{r}
chile_joined %>% 
  select(species) %>% 
  unique()
```

## Filter for max. range < 3000m
```{r}
# chile_range <- 
chile_j_elev <- chile_joined %>% 
  filter(`6.1.2` < 3000) #%>% 
  # distinct(species, .keep_all = TRUE)
```

## Filter ranges
When we have two entries with different ranges, we take the smaller minimum and bigger maximum
```{r}
min_spec <- chile_j_elev %>% 
  group_by(species) %>% 
  filter(n() > 1) %>% 
  mutate(min = min(`6.1.1`)) %>% 
  distinct(species, .keep_all = TRUE)
```

```{r}
max_spec <- chile_j_elev %>% 
  group_by(species) %>% 
  filter(n() > 1) %>% 
  ungroup() %>% 
  mutate(max = max(`6.1.2`)) %>% 
  distinct(species, .keep_all = TRUE)
```

```{r}
max_spec_sel <- max_spec %>% 
  select(species, max)

new_species_range <- full_join(min_spec, max_spec_sel, by = "species")
```

```{r}
chile_unique <- chile_j_elev %>% 
  group_by(species) %>% 
  filter(n() == 1) %>% 
  mutate(min = `6.1.1`,
         max = `6.1.2`)
```

```{r}
chile_final <- rbind(chile_unique, new_species)

chile_final %>% 
  filter(is.na(ref_ID.y))
```

save updated datatable
```{r}
write.csv(chile_final, here::here("./data/chile_updated_checklist.csv"), na = "")
```

