---
title: "B1_NonGiftChecklist_1"
author: "Johanna Klapper"
date: "4/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading packages
```{r, message=FALSE}
library(tidyverse)
library(readxl)
```

In this script, the checklists that are not yet in GIFT will be prepared to be later on merged together.
For this, the following steps will be necessary:
  - add column with desert/area name
  - remove unused columns (columns with no values in all checklists)
  - adjust column names
  - some checklists have to be manually adjusted, e.g. China with cm and m values
  
The following columns will be used for the dataset:
  - desert
  - species
  - native
  - endemic
  - alien
  - growth_form
  - lifecycle
  - lifeform
  - liana
  - climber
  - aquatic
  - succulence
  - plant_height_min
  - plant_height_max
  - rhizome_length
  - min_elevation
  - max_elevation
  - blooming_season
  - habitat

# Checklists (not in GIFT format)

## China

```{r}
china <- read_excel(here::here('./data/checklists/original/China.xlsx'), sheet = 2)
```

The minimum and maximum height of plants have some cm and m values in them, with the following code I'm transforming cm into m
```{r}
min_height <- str_split_fixed(china$plant_height_min, " ", n = 2) %>% 
  as_tibble() %>% 
  rename(height = V1,
         unit = V2)

china_2 <- bind_cols(china, min_height)

china_21 <- china_2 %>% 
  filter(unit == "cm") %>% 
  mutate(height = parse_number(height),
    height = height * 0.01)

china_22 <- china_2 %>% 
  filter(unit != "cm") %>% 
  mutate(height = parse_number(height))

china_3 <- bind_rows(china_21, china_22) %>% 
  select(-c(plant_height_min, unit, plant_height_max)) %>% 
  rename(plant_height_min = height)



max_height <- str_split_fixed(china$plant_height_max, " ", n = 2) %>% 
  as_tibble() %>% 
  rename(height = V1,
         unit = V2)

china_4 <- bind_cols(china, max_height)

china_41 <- china_4 %>% 
  filter(unit == "cm") %>% 
  mutate(height = parse_number(height),
         height = height * 0.01) %>% 
  select(-plant_height_max)

china_42 <- china_4 %>% 
  filter(unit != "cm") %>% 
  mutate(height = parse_number(height))

china_5 <- bind_rows(china_41, china_42) %>% 
  select(-c(plant_height_max, unit, plant_height_min)) %>% 
  rename(plant_height_max = height) 



china_6 <- full_join(china_3, (china_5 %>% select(plant_height_max, species_fullname)), by = "species_fullname")
```


```{r}
china_proc <- china_6 %>% 
  mutate(desert = "China",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA) %>% 
  mutate_at(c("endemic", "native"), as.character) %>% 
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = species_fullname,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         liana = Liana,
         climber = Climber,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_ Chinese`))
```



## China - Tengger Desert

```{r}
china_tengger <- read_excel(here::here("./data/checklists/original/China_TenggerDesert.xlsx"), sheet = 2)
```

```{r}
china_tengger_proc <- china_tengger %>% 
  mutate(desert = "China_TenggerDesert",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```



## Egypt Wadi Allaqi

```{r}
egypt <- read_excel(here::here("./data/checklists/original/Egypt_Wadi_Allaqi.xlsx"), sheet = 2)
```

```{r}
egypt_proc <- egypt %>% 
  mutate(desert = "Egypt",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```



## Iran Fereizi

```{r}
iran_fereizi <- read_excel(here::here("./data/checklists/original/Iran_Fereizi.xlsx"), sheet = 2)
```

```{r}
iran_fereizi_proc <- iran_fereizi %>% 
  mutate(desert = "Iran Fereizi",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```


## Iran Heydari Wildlife Refuge

```{r}
iran_heydari <- read_excel(here::here("./data/checklists/original/Iran_Heydari_Wildlife_Refuge.xlsx"), sheet = 2)
```

```{r}
iran_heydari_proc <- iran_heydari %>% 
  mutate(desert = "Iran Heydari",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```


## Iran Isfahan Province

```{r}
iran_isfahan <- read_excel(here::here("./data/checklists/original/Iran_Isfahan_Province.xlsx"), sheet = 2)
```

```{r}
iran_isfahan_proc <- iran_isfahan %>% 
  mutate(desert = "Iran Isfahan Province",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```


## Iran Kavir Protected Region

```{r}
iran_kavir <- read_excel(here::here("./data/checklists/original/Iran_Kavir_Protected_Region.xlsx"), sheet = 2)
```

```{r}
iran_kavir_proc <- iran_kavir %>% 
  mutate(desert = "Iran Kavir Region",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```


## Iran Sistan Baluchestan Province

```{r}
iran_sistan_baluchestan <- read_excel(here::here("./data/checklists/original/Iran_Sistan_Baluchestan_Province.xlsx"), sheet = 2)
```

```{r}
iran_sistan_baluchestan_proc <- iran_sistan_baluchestan %>% 
  mutate(desert = "Iran Sistan Baluchestan Province",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```


## Iran Southern Khorasan

```{r}
iran_southern_khorasan <- read_excel(here::here("./data/checklists/original/Iran_Southern_Khorasan.xlsx"), sheet = 2)
```

```{r}
iran_southern_khorasan_proc <- iran_southern_khorasan %>% 
  mutate(desert = "Iran Southern Khorasan",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```


## Iran Touran Protected Area

```{r}
iran_touran <- read_excel(here::here("./data/checklists/original/Iran_Touran_Protected_Area.xlsx"), sheet = 2)
```

```{r}
iran_touran_proc <- iran_touran %>% 
  mutate(desert = "Iran Touran Area",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```


## Iran Yahya Abad

```{r}
iran_yahya_abad <- read_excel(here::here("./data/checklists/original/Iran_YahyaAbad.xlsx"), sheet = 2)
```

```{r}
iran_yahya_abad_proc <- iran_yahya_abad %>% 
  mutate(desert = "Iran Yahya Abad",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```


## Libya Tanezzuft

```{r}
libya_tanezzuft <- read_excel(here::here("./data/checklists/original/Libya_Tanezzuft.xlsx"), sheet = 1)
```

```{r}
libya_tanezzuft_proc <- libya_tanezzuft %>% 
  mutate(desert = "Libya_Tanezzuft",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon, `JarJar Amma`, Tanezzuft))
```


## Mauritania Assaba

```{r}
mauritania <- read_excel(here::here("./data/checklists/original/Mauritania_Assaba.xlsx"), sheet = 2)
```

```{r}
mauritania_proc <- mauritania %>% 
  mutate(desert = "Mauritania_Assaba",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```


## Mexican Coahuila - Sierra de la Paila

```{r}
mexico_paila <- read_excel(here::here("./data/checklists/original/MexicanCoahuila_SierraDeLaPaila.xlsx"), sheet = 2)
```

```{r}
mexico_paila_proc <- mexico_paila %>% 
  mutate(desert = "MexicanCoahuila_SierraDeLaPaila",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```


## Mexican Coahuila - Sierra de la Zapalina

```{r}
mexico_zapalina <- read_excel(here::here("./data/checklists/original/MexicanCoahuila_SierraDeLaZapalina.xlsx"), sheet = 2)
```

```{r}
mexico_zapalina_proc <- mexico_zapalina %>% 
  mutate(desert = "MexicanCoahuila_SierraDeLaZapalina",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```


## Namib Desert

```{r}
namib <- read_excel(here::here("./data/checklists/original/Namib_Desert.xlsx"), sheet = 1)
```

```{r}
namib_proc <- namib %>% 
  mutate(desert = "NamibDesert",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%
  rename(species = species_original,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic,
         endemic = endemicndendemicmic) %>%   
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  select(-c(root_depth_min, root_depth_max, full_description, `full_description_translated`, species_full_name, genus, species_epithet, author, subtaxon, Photosynthetic_pathway))
```



## Namib Desert - Gobabeb

```{r}
namib_gobabeb <- read_excel(here::here("./data/checklists/original/NamibDesert_Gobabeb.xlsx"), sheet = 1)
```

```{r}
namib__gobabeb_proc <- namib_gobabeb %>% 
  unite(species, c(Species, Author), sep = " ") %>% 
  mutate(desert = "NamibDesert_Gobabeb",
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         liana = NA,
         climber = NA,
         endemic = NA,
         native = NA,
         growth_form = NA,
         lifecycle = NA,
         aquatic = NA,
         plant_height_min = NA,
         plant_height_max = NA,
         succulence = NA) %>%
  rename(lifeform = Perennial,
         habitat = Habitat,
         alien = Alien) %>%   
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  select(-Family)
```



## North America - Sonoran Desert

```{r}
sonoran <- read_excel(here::here("./data/checklists/original/NorthAmerica_Sonoran_Desert.xlsx"), sheet = 4)
```

```{r}
sonoran_proc <- sonoran %>%
  select(-species) %>% 
  mutate(desert = "NorthAmerica_SonoranDesert",
         alien = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%
  rename(species = species_orig,
         native = native...3,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>%   
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  select(-c(list_ID, species_full:`1.5.1`))
```



## North America - Great Basin

```{r}
greatbasin <- read_excel(here::here("./data/checklists/original/NorthAmerica_Great_Basin.xlsx"), sheet = 2)
```

```{r}
greatbasin_proc <- greatbasin %>% 
  mutate(desert = "NorthAmerica_GreatBasin",
         alien = NA,
         rhizome_length = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic,
         habitat = `habitat/notes`,
         blooming_season = `blooming season`) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon)) %>% 
  mutate(min_elevation = 0.3048 * min_elevation,
         max_elevation = 0.3048 * max_elevation)
```



## Peru

```{r}
peru <- read.csv(here::here("./data/checklists/original/Peru.csv"))
```

```{r}
peru_proc <- peru %>% 
  mutate(desert = "Peru",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA,
         endemic = NA,
         native = NA,
         growth_form = NA,
         lifecycle = NA,
         aquatic = NA,
         lifeform = NA,
         plant_height_min = NA,
         plant_height_max = NA,
         succulence = NA) %>% 
  mutate_at(c("endemic", "native"), as.character) %>% 
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = Name) %>% 
  select(-NameID)
```



## Sahara Desert - Air Massif

```{r}
airmassif <- read_excel(here::here("./data/checklists/original/Sahara_Desert_Aïr_Massif.xlsx"), sheet = 2)
```

```{r}
airmassif_proc <- airmassif %>% 
  mutate(desert = "SaharaDesert_AirMassif",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>% 
  mutate_at(c("endemic", "native"), as.character) %>% 
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```


## Sahara Desert 

```{r}
sahara <- read_excel(here::here("./data/checklists/original/Sahara_Desert.xlsx"), sheet = 2)
```

```{r}
sahara_proc <- sahara %>% 
  mutate(desert = "SaharaDesert",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```


## Sahara Desert - Jebel Uweinat

```{r}
jebel <- read_excel(here::here("./data/checklists/original/Sahara_Desert_Jebel_Uweinat.xlsx"))
```

```{r}
jebel_proc <- jebel %>% 
  mutate(desert = "SaharaDesert_JebelUweinat",
         alien = NA,
         rhizome_length = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA,
         endemic = NA,
         native = NA,
         growth_form = NA,
         lifecycle = NA,
         aquatic = NA,
         plant_height_min = NA,
         plant_height_max = NA,
         succulence = NA) %>% 
  rename(species = Species,
         lifeform = Biological_type) %>% 
  select(-c(Family, Grazed)) %>% 
  separate(col = Elevation_range, c('min_elevation', 'max_elevation')) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric)
```


## Sudan - Khartoum State

```{r}
sudan <- read_excel(here::here("./data/checklists/original/Sudan_Khartoum_State.xlsx"), sheet = 2)
```

```{r}
sudan_proc <- sudan %>% 
  mutate(desert = "Sudan_KhartoumState",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```


## Tibesti

```{r}
tibesti <- read_excel(here::here("./data/checklists/original/Tibesti.xlsx"), sheet = 2)
```

```{r}
tibesti_proc <- tibesti %>% 
  mutate(desert = "Tibesti",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA,
         lifeform = NA,
         lifecycle = NA,
         aquatic = NA,
         plant_height_min = NA,
         plant_height_max = NA,
         succulence = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = species_full)
```


## Uzbekistan - Vozrozhdeniya Island

```{r}
uzbekistan <- read_excel(here::here("./data/checklists/original/Uzbekistan_Vozrozhdeniya_Island.xlsx"), sheet = 2)
```

```{r}
uzbekistan_proc <- uzbekistan %>% 
  mutate(desert = "Uzbekistan_VozrozhdeniyaIsland",
         alien = NA,
         rhizome_length = NA,
         min_elevation = NA,
         max_elevation = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA) %>%  
  mutate_at(c("endemic", "native"), as.character) %>%
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  rename(species = `species_full name`,
         growth_form = Growth_form,
         lifecycle = Lifecycle,
         lifeform = Lifeform,
         aquatic = Aquatic) %>% 
  select(-c(root_depth_min, root_depth_max,`Photosynthetic pathway`, full_description, `full_description_translated`, species_original, genus, species_epithet, author, subtaxon))
```




# Binding processed datasets

In this section, I will bind the datasets that now have the same amount and names of columns. The function 'bind_rows' from the dplyr package will be used as for this function the datasets do not have to have the same order of columns.

```{r}
data_full <- mget(ls(envir = globalenv(), pattern = "proc$")) %>% 
  bind_rows()
```

The columns that will be needed to split the names and do some formatting have to be added:
"species" (already exists)
"species_full" 
"genus"
"cf_genus"
"species_epithet"
"cf_species"
"author"
"subtaxon"
"subt_author"
"hybrid"

```{r}
data_full <- data_full %>% 
  mutate(species_full = species,
         genus = NA,
         cf_genus = NA,
         species_epithet = NA,
         cf_species = NA,
         author = NA,
         subtaxon = NA,
         subt_author = NA,
         hybrid = NA,
         species = NA)
```

# Save the dataset
```{r}
write.csv(data_full, here::here("./data/checklists/processed/data_full.csv"), row.names = FALSE)
```



# Load data in case of any changes later on
```{r}
#data_full <- read.csv(here::here("./data/checklists/processed/data_full.csv"))
```


