---
title: "B2_NonGiftChecklists_2"
author: "Johanna Klapper"
date: "4/29/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The dataset from 'B1_NonGiftChecklists_1.Rmd' was processed with 'split_names_proc.R' to split the species name and authors.
After combining all checklists from outside GIFT, there are still some entries which have to be adjusted, e.g. different entries for endemic species.
Checklists that are already in GIFT format, but not yet in GIFT will be added to the dataset.
Finally, the species names will be taxonomically standardized with The Plant List.


# Load packages
```{r}
library(tidyverse)
library(Taxonstand)
```


# Load dataset from outside GIFT
```{r}
dataset <- read.csv(here::here("./data/checklists/processed/data_full_procNames.csv"), header = TRUE)
```


# Adjust entries in endemic column: endemic - 1, not endemic - 0 and create one column which will be used to connect data + polygon
```{r}
dataset <- dataset %>% 
  mutate(endemic = if_else(endemic %in% c("1", "(yes)", "yes", "endemic"), 1, 0),
         polygon = desert)
```



# Add checklists that have already been processed (in GIFT format, not in GIFT)
  
## Chile
```{r}
chile <- read.csv(here::here("./data/checklists/original/Chile.csv"))
```

```{r}
chile_proc <- chile %>% 
  filter(list_ID != "NA",
         species != "Zostera chilensis") %>% # not a desert species
  mutate(desert = "Chile",
         alien = NA,
         growth_form = NA,
         lifecycle = NA,
         lifeform = NA,
         liana = NA,
         climber = NA,
         aquatic = NA,
         succulence = NA,
         plant_height_min = NA,
         plant_height_max = NA,
         rhizome_length = NA,
         blooming_season = NA,
         habitat = NA,
         species_full = NA,
         genus = NA,
         cf_genus = NA,
         species_epithet = NA,
         cf_species = NA,
         aff_species = NA,
         author = NA,
         subtaxon = NA,
         subt_author = NA,
         hybrid = NA,
         endemic = NA) %>%  
  mutate_at("native", as.character) %>% 
  rename(polygon = geo_entity_ref,
         min_elevation = X6.1.1,
         max_elevation = X6.1.2) %>% 
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  select(-c(X, list_ID, ref_ID.x, entity_ID, work_ID.x, questionable, quest_native, naturalized, endemic_ref, quest_end_ref, endemic_list, quest_end_list, cons_status, ref_ID.y, orig_ID, name_ID, work_ID.y, taxon_ID, X6.1.3))
```


## Farasan Archipelago
```{r}
farasan <- read.csv(here::here("./data/checklists/original/Farasan_Archipelago.csv"))
```

```{r}
farasan_proc <- farasan %>% 
  mutate(desert = "Farasan",
         alien = NA,
         growth_form = NA,
         lifecycle = NA,
         lifeform = NA,
         liana = NA,
         climber = NA,
         aquatic = NA,
         succulence = NA,
         plant_height_min = NA,
         plant_height_max = NA,
         rhizome_length = NA,
         blooming_season = NA,
         habitat = NA,
         min_elevation = NA,
         max_elevation = NA,
         endemic = NA) %>%  
  mutate_at("native", as.character) %>% 
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  select(-c(list_ID, questionable, quest_native, naturalized, endemic_ref, quest_end_ref, endemic_list, quest_end_list, cons_status))
```


This dataset has to be divided into the different islands, since species are recorded for the different islands.

```{r}
farasan_alkabir <- subset(farasan_proc, Farasan.Al.Kabir == "1") %>% 
  mutate(desert = "Farasan_AlKabir",
         polygon = desert) %>% 
  select(-c(Farasan.Al.Kabir, Sajid, Zifaf, Qummah, Dumsuq, Dushak))

farasan_sajid <- subset(farasan_proc, Sajid == "1") %>% 
  mutate(desert = "Farasan_Sajid",
         polygon = desert) %>% 
  select(-c(Farasan.Al.Kabir, Sajid, Zifaf, Qummah, Dumsuq, Dushak))

farasan_zifaf <- subset(farasan_proc, Zifaf == "1") %>% 
  mutate(desert = "Farasan_Zifaf",
         polygon = desert) %>% 
  select(-c(Farasan.Al.Kabir, Sajid, Zifaf, Qummah, Dumsuq, Dushak))

farasan_qummah <- subset(farasan_proc, Qummah == "1") %>% 
  mutate(desert = "Farasan_Qummah",
         polygon = desert) %>% 
  select(-c(Farasan.Al.Kabir, Sajid, Zifaf, Qummah, Dumsuq, Dushak))

farasan_dumsuq <- subset(farasan_proc, Dumsuq == "1") %>% 
  mutate(desert = "Farasan_Dumsuq",
         polygon = desert) %>% 
  select(-c(Farasan.Al.Kabir, Sajid, Zifaf, Qummah, Dumsuq, Dushak))

farasan_dushak <- subset(farasan_proc, Dushak == "1") %>% 
  mutate(desert = "Farasan_Dushak",
         polygon = desert) %>% 
  select(-c(Farasan.Al.Kabir, Sajid, Zifaf, Qummah, Dumsuq, Dushak))
```

```{r}
write.csv(farasan_alkabir, here::here("./data/checklists/original/Farasan_AlKabir.csv"))
write.csv(farasan_dumsuq, here::here("./data/checklists/original/Farasan_Dumsuq.csv"))
write.csv(farasan_dushak, here::here("./data/checklists/original/Farasan_Dushak.csv"))
write.csv(farasan_qummah, here::here("./data/checklists/original/Farasan_Qummah.csv"))
write.csv(farasan_sajid, here::here("./data/checklists/original/Farasan_Sajid.csv"))
write.csv(farasan_zifaf, here::here("./data/checklists/original/Farasan_Zifaf.csv"))
```


## India
```{r}
india <- readxl::read_excel(here::here("./data/checklists/original/India.xlsx"), sheet = 6)
```

```{r}
india_proc <- india %>% 
  mutate(desert = "India",
         polygon = desert,
         plant_height_min = `1.6.1`,
         plant_height_max = `1.6.2`,
         endemic = NA,
         min_elevation = NA,
         max_elevation = NA,
         rhizome_length = NA,
         blooming_season = NA,
         habitat = NA,
         liana = NA,
         climber = NA,
         alien = NA) %>%
  select(-succulence) %>% 
  rename(growth_form = `1.2.2`,
         lifecycle = `2.1.1`,
         succulence = `4.16.1`,
         aquatic = `1.7.1`,
         lifeform = Lifeform) %>%  
  mutate_at("native", as.character) %>% 
  mutate_at(c("min_elevation", "max_elevation"), as.numeric) %>% 
  select(-c(list_ID, species_original, Growth_form, Lifecycle, Aquatic, parasite, orig_1, `1.6.1`, orig_2, `1.6.2`, orig_3, `1.4.2`, orig_4, orig_5, orig_6, orig_7, `1.5.1`, questionable, quest_native, naturalized, endemic_ref, quest_end_ref, endemic_list, quest_end_list, cons_status))
```


## Join previous dataset with new checklists and remove aquatic species

```{r}
dataset_proc <- dataset %>% 
  bind_rows(chile_proc, farasan_alkabir, farasan_dumsuq, farasan_dushak, farasan_qummah, farasan_sajid, farasan_zifaf, india_proc) %>% 
  filter(aquatic == "" | is.na(aquatic) | aquatic == "terrestrial")
```


# Harmonize species names with PlantList
```{r}
taxstand <- TPL(genus = dataset_proc$genus, species = dataset_proc$species_epithet, diffchar = 2, max.distance = 1)

taxstand_copy <- taxstand

for (i in 1:nrow(taxstand)){
  dataset_proc$genus[which(dataset_proc$genus == taxstand$Genus[i] &
                        dataset_proc$species_epithet == taxstand$Species[i])] <- taxstand$New.Genus[i]
  dataset_proc$species_epithet[which(dataset_proc$genus == taxstand$Genus[i] &
                          dataset_proc$species_epithet == taxstand$Species[i])] <- taxstand$New.Species[i]
}


write.csv(taxstand, here::here("./data/checklists/processed/data_taxstand.csv"))
write.csv(taxstand_copy, here::here("./data/checklists/processed/data_taxstand_copy.csv"))
```



# Save dataset
```{r}
write.csv(dataset_proc, here::here("./data/checklists/processed/dataset_proc.csv"), row.names = FALSE)
```

