---
title: "B3_NonGiftPolygons"
author: "Johanna Klapper"
date: "5/11/2022"
output: html_document
---

This Markdown will combine the checklists from outside GIFT with the respective polygons.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(sf)
library(exactextractr)
library(raster)
```


# Load data
```{r}
dataset <- read.csv(here::here("./data/checklists/processed/dataset_proc.csv"), header = TRUE)
```

```{r}
path <- c(here::here("./data/polygons/"))
setwd(path)

polygon_names <- list.files(path = path, pattern = "\\.shp$")        # Get all file names
polygon_names                                                        # Return file names to console

polygon_list <- sapply(polygon_names, function(x) read_sf(x), USE.NAMES = TRUE)  # Read all shapefiles

list2env(polygon_list,.GlobalEnv)  # Unlist shapefile list
rm(polygon_list)
```


# Clip polygons for Chile and Peru to < 3000m
```{r}
mean_alt <- raster(here::here("./data/analysis/rasters/mn30_grd/w001001.adf"))

chile <- st_transform(Chile.shp, crs(mean_alt))
raster_chile <- crop(mean_alt, chile)
raster_chile_mask <- mask(raster_chile, chile)
raster_chile_clip <- raster_chile_mask < 3000
raster_chile_shp <- rasterToPolygons(raster_chile_clip, dissolve = TRUE)
Chile.shp <- st_as_sf(raster_chile_shp) %>% 
  filter(layer == 1)

peru <- st_transform(PER_CoastDesert.shp, crs(mean_alt))
raster_peru <- crop(mean_alt, peru)
raster_peru_mask <- mask(raster_peru, peru)
raster_peru_clip <- raster_peru_mask < 3000
raster_peru_shp <- rasterToPolygons(raster_peru_clip, dissolve = TRUE)
PER_CoastDesert.shp <- st_as_sf(raster_peru_shp) %>% 
  filter(layer == 1)
```


# Prepare data, i.e. adjust names of polygons

## Add name of desert
```{r}
Air_mountains.shp <- Air_mountains.shp %>% 
  mutate(desert = "SaharaDesert_AirMassif")

AralIsland_Uzbek.shp <- AralIsland_Uzbek.shp %>% 
  mutate(desert = "Uzbekistan_VozrozhdeniyaIsland")

Binalood.shp <- Binalood.shp %>% 
  mutate(desert = "Iran Fereizi")

Central_Namib_polygon.shp <- Central_Namib_polygon.shp %>% 
  mutate(desert = "NamibDesert")

Chile.shp <- Chile.shp %>% 
  mutate(desert = "Chile") %>% 
  st_transform(crs = st_crs(Air_mountains.shp))

China_desert_dis.shp <- China_desert_dis.shp %>% 
  mutate(desert = "China")

China_TenggerDesert.shp <- China_TenggerDesert.shp %>% 
  mutate(desert = "China_TenggerDesert")

Dumsuq.shp <- Dumsuq.shp %>% 
  mutate(desert = "Farasan_Dumsuq")

Dushak.shp <- Dushak.shp %>% 
  mutate(desert = "Farasan_Dushak")

Egypt_Wadi_Allaqi_NR.shp <- Egypt_Wadi_Allaqi_NR.shp %>% 
  mutate(desert = "Egypt")

El_Rawakeeb_Flora_Sudan.shp <- El_Rawakeeb_Flora_Sudan.shp %>% 
  mutate(desert = "Sudan_KhartoumState")

`Farasan Al Kabir.shp` <- `Farasan Al Kabir.shp` %>% 
  mutate(desert = "Farasan_AlKabir")

Flora_Assaba_Mauritanie.shp <- Flora_Assaba_Mauritanie.shp %>% 
  mutate(desert = "Mauritania_Assaba")

Gobabeb_try.shp <- Gobabeb_try.shp %>% 
  mutate(desert = "NamibDesert_Gobabeb")

GreatBasinNP.shp <- GreatBasinNP.shp %>% 
  mutate(desert = "NorthAmerica_GreatBasin")

Heydari.shp <- Heydari.shp %>% 
  mutate(desert = "Iran Heydari")

Indian_desert.shp <- Indian_desert.shp %>% 
  mutate(desert = "India")

Iran_IsfahanProvince.shp <- Iran_IsfahanProvince.shp %>% 
  mutate(desert = "Iran Isfahan Province")

Iran_SistanRegion.shp <- Iran_SistanRegion.shp %>% 
  mutate(desert = "Iran Sistan Baluchestan Province")

Iran_SouthernKhorasan.shp <- Iran_SouthernKhorasan.shp %>% 
  mutate(desert = "Iran Southern Khorasan")

Iran_YahyaAbad_2.shp <- Iran_YahyaAbad_2.shp %>% 
  mutate(desert = "Iran Yahya Abad")

Jebel_Uweinat.shp <- Jebel_Uweinat.shp %>% 
  mutate(desert = "SaharaDesert_JebelUweinat")

Kavir.shp <- Kavir.shp %>% 
  mutate(desert = "Iran Kavir Region")

Libya.shp <- Libya.shp %>% 
  mutate(desert = "Libya_Tanezzuft")

Ozenda_flora_zoneA.shp <- Ozenda_flora_zoneA.shp %>% 
  mutate(desert = "SaharaDesert")

PER_CoastDesert.shp <- PER_CoastDesert.shp %>% 
  mutate(desert = "Peru")

Qummah.shp <- Qummah.shp %>% 
  mutate(desert = "Farasan_Qummah")

Sajid.shp <- Sajid.shp %>% 
  mutate(desert = "Farasan_Sajid")

SierraDeLaPaila_Mexico.shp <- SierraDeLaPaila_Mexico.shp %>% 
  mutate(desert = "MexicanCoahuila_SierraDeLaPaila")

SierradeZapalinameCoahuila.shp <- SierradeZapalinameCoahuila.shp %>% 
  mutate(desert = "MexicanCoahuila_SierraDeLaZapalina")

Sonoran_dis.shp <- Sonoran_dis.shp %>% 
  mutate(desert = "NorthAmerica_SonoranDesert")

Tibesti.shp <- Tibesti.shp %>% 
  mutate(desert = "Tibesti")

Touran.shp <- Touran.shp %>% 
  mutate(desert = "Iran Touran Area")

Zifaf.shp <- Zifaf.shp %>% 
  mutate(desert = "Farasan_Zifaf")
```


# Join polygons with dataset
```{r}
polygons <- mget(ls(envir = globalenv(), pattern = "\\.shp$"))
```

```{r}
saveRDS(polygons, here::here("./data/analysis/polygons.RData"))
```

```{r}
#polygons <- readRDS(here::here("./data/analysis/polygons.RData"))
```



# Determine whether polygons are within arid/biome regions
```{r}
# Biomes
biomes <- read_sf(here::here("data/gis_data/biomes/Ecoregions2017/Ecoregions2017.shp"))

# Arid areas
arid <- raster(here::here("data/gis_data/global-ai_et0/ai_et0/ai_et0.tif"))
```


## Sonoran, Peru, Chile and China polygons consist of multiple polygons -> combine them, otherwise R will give errors
```{r}
Sonoran_dis.shp <- st_cast(Sonoran_dis.shp, "POLYGON")

China_desert_dis.shp <- st_cast(China_desert_dis.shp, "POLYGON")

PER_CoastDesert.shp <- st_cast(PER_CoastDesert.shp, "POLYGON")

Chile.shp <- st_cast(Chile.shp, "POLYGON")
```

```{r}
polygons <- mget(ls(envir = globalenv(), pattern = "\\.shp$"))
```

## Arid regions
```{r}
mean_arid_extract <- lapply(polygons, function(x) exact_extract(arid,x,fun=c("mean", "stdev")))

mean_arid_df <- do.call(rbind.data.frame, mean_arid_extract)

table(mean_arid_df$mean < 2000)

# 30 polygons fall within arid definition, 4 not

no_arid <- lapply(mean_arid_extract, function(x) filter(x, mean > 2000)) 
no_arid <- do.call(rbind.data.frame, no_arid)

# Binalood.shp
# GreatBasinNP.shp
# Heydari.shp
# SierradeZapalinameCoahuila.shp
```

## Biome regions
```{r}
sf::sf_use_s2(FALSE)

# Test run -> working

#test <- st_intersection(Air_mountains.shp, biomes)
#test$area <- st_area(test)
#test %>% 
#  mutate_at(c("area"), as.numeric) %>% 
#  slice(which.max(area))


# Intersect with sf package
intersec <- lapply(polygons, function(x) st_intersection(x, biomes))

# Calculate area and filter for max area and biome type
biome_list <- lapply(intersec, function(x) slice(x, which.max(SHAPE_AREA)))
biome_list_df <- list2DF(biome_list)

# Air_mountains: Tropical & Subtropical Grasslands, Savannas & Shrublands
# Central Namib Polygon: Tropical & Subtropical Grasslands, Savannas & Shrublands
# El_Rawakeeb_Flora_Sudan: Tropical & Subtropical Grasslands, Savannas & Shrublands
# Flora_Assaba_Mauritanie: Tropical & Subtropical Grasslands, Savannas & Shrublands
# Chile: Montane Grasslands & Shrublands
# China_desert: Temperate Grasslands, Savannas & Shrublands
# Peru: Montane Grasslands & Shrublands
# Everything else: Deserts & Xeric Shrublands
```


## Add column with arid/biome information

Chile: desert_arid
China: desert_arid
China_TenggerDesert: desert
Egypt: desert
Farasan_AlKabir: desert
Farasan_Sajid: desert
Farasan_Zifaf: desert
Farasan_Qummah: desert
Farasan_Dumsuq: desert
Farasan_Dushak: desert
India: desert
Iran Fereizi: desert_biome
Iran Heydari: desert_biome
Iran Isfahan Province: desert
Iran Kavir Region: desert
Iran Sistan Baluchestan Province: desert
Iran Southern Khorasan: desert
Iran Touran Area: desert
Iran Yahya Abad: desert
Libya: desert
Mauritania_Assaba: desert_arid
MexicanCoahuila_SierraDeLaPaila: desert
MexicanCoahuila_SierraDeLaZapalina: desert_biome
NamibDesert: desert_arid
NamibDesert_Gobabeb: desert
NorthAmerica_SonoranDesert: desert
NorthAmerica_GreatBasin: desert_biome
Peru: desert_arid
SaharaDesert_AirMassif: desert_arid
SaharaDesert: desert
SaharaDesert_JebelUweinat: desert
Sudan_KhartoumState: desert_arid
Tibesti: desert
Uzbekistan_VozrozhdeniyaIsland: desert


```{r}
polygons_arid <- c("Chile", "China", "Mauritania_Assaba", "NamibDesert", "Peru", "SaharaDesert_AirMassif", "Sudan_KhartoumState")
polygons_biome <- c("Iran Fereizi", "Iran Heydari", "MexicanCoahuila_SierraDeLaZapalina", "NorthAmerica_GreatBasin")
```

```{r}
polygons_df <- sf::st_as_sf(data.table::rbindlist(polygons, fill = TRUE)) %>% 
  dplyr::select(desert, geometry)

polygons_df$desert_both <- ifelse(polygons_df$desert %in% polygons_arid, 'desert_arid', ifelse(polygons_df$desert %in% polygons_biome, 'desert_biome', 'desert'))
```


## Add column with island/mainland category
```{r}
polygons_island <- c("Farasan_AlKabir", "Farasan_Sajid", "Farasan_Zifaf", "Farasan_Qummah", "Farasan_Dumsuq", "Farasan_Dushak")
polygons_df$island.mainland <- ifelse(polygons_df$desert %in% polygons_island, "Island", "Mainland")
```


## Save polygon information
```{r}
write_sf(polygons_df, here::here("./data/analysis/non_gift_checklists.shp"))
```
