---
title: "DesertMapping"
author: "Johanna Klapper"
date: "4/28/2022"
output: html_document
---

This Markdown contains:
- area analysis for desert definitions
- area analysis for checklists and regions
- map plotting of desert definitions, checklists and regions


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load packages
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(sp)
library(rgdal)
library(raster)
library(sf)
library(ggthemes)
library(rnaturalearth)
library(rnaturalearthdata)
```


# Load data
```{r}
# Coastlines of the world
world_coast <- ne_coastline(scale = "medium", returnclass = "sf")

# coarse arid raster file
arid_coarse <- raster(here::here("data/gis_data/global-ai_et0/ai_et0/arid_coarse.tif"))

# Polygons data
polygons_data <- read_sf(here::here("./data/analysis/polygons_data.shp"))

# Biomes
biomes <- read_sf(here::here("data/gis_data/biomes/Ecoregions2017/Ecoregions2017.shp"))
```



# Data preparation

## Limit biomes to desert biome
```{r}
# Visualize biomes
desert_biomes <- biomes[biomes$BIOME_NUM == 13, ] %>% 
  st_make_valid()
```

## Transform aridity raster into shapefile
```{r}
# prepare aridity raster to plot with ggplot
library(stars)
arid_plot <- read_stars(here::here("./data/gis_data/global-ai_et0/ai_et0/arid_coarse.tif"))
arid_sf <- st_as_sf(arid_plot, as_points = FALSE, merge = TRUE)
```

## Intersect areas of both definitions
```{r}
# prepare spatial data to create one shapefile for each definition and their overlap
desert_biomes_raster <- rasterize(desert_biomes, arid_coarse)

# Overlap
desert_both_raster <- mask(arid_coarse, desert_biomes_raster)
desert_both <- st_intersection(arid_sf, desert_biomes)

# Only aridity
arid_only <- mask(arid_coarse, as_Spatial(desert_biomes), inverse = TRUE)
arid_only_sf <- raster::rasterToPolygons(arid_only) %>% 
  st_as_sf()

# only biome
biome_only <- mask(desert_biomes_raster, as_Spatial(arid_sf), inverse = TRUE)
biome_only_sf <- raster::rasterToPolygons(biome_only) %>% 
  st_as_sf()
```

## Combine polygons to one layer/raster
```{r}
one_polygon <- st_make_valid(polygons_data) %>% 
  st_union() %>% 
  st_as_sf()

one_polygon %>% 
  st_make_valid() %>% 
  st_area()

polygon_raster <- sf::as_Spatial(one_polygon) %>% 
  rasterize(y = arid_coarse)
```


## Combine areas of both definitions
```{r}
deserts <- rbind(desert_biomes$geometry, arid_sf$geometry)
deserts <- summarise(deserts)
```


# Data analysis

## Area of each definition
```{r}
arid_sf %>% 
  st_union() %>% 
  st_area()
# 4.194556e+13 [m^2]

desert_biomes %>% 
  st_union() %>% 
  st_area()
#2.632273e+13 [m^2]

desert_both_sf %>% 
  st_make_valid() %>% 
  st_union() %>% 
  st_area()
#2.511461e+13 [m^2]
```


## Number of checklists per region
```{r}
polygons_data %>% 
  distinct(desert, .keep_all = TRUE) %>% 
  group_by(contnnt) %>% 
  summarise(n = n())

#Asia	41			
#North Africa	18			
#North America	48			
#Oceania	22			
#South Africa	5		
#South America	29
```


## Calculating the percentage of coverage of checklists for biome and arid regions

### Aridity
```{r}
cov_arid_ch <- mask(crop(polygon_raster, arid_coarse), arid_coarse) 
  
area_arid_ch <- as.data.frame(cov_arid_ch, na.rm = TRUE) %>%
      tally() %>%
      mutate(area = n * res(cov_arid_ch)[1] * res(cov_arid_ch)[2]) %>% 
      dplyr::select(area)

area_arid_ch$area / area_arid$area

# 0.3528407 (of arid areas covered)
```

### Biome
```{r}
cov_biome_ch <- mask(crop(polygon_raster, desert_biomes_raster), desert_biomes_raster) 
  
area_biome_ch <- as.data.frame(cov_biome_ch, na.rm = TRUE) %>%
      tally() %>%
      mutate(area = n * res(cov_biome_ch)[1] * res(cov_biome_ch)[2]) %>% 
      dplyr::select(area)

#area_pol_biome <- sum(unlist(area_biome_ch))

area_biome_ch$area / area_biome$area

# 0.4825926 (of biome areas covered)
```

### Overlap
```{r}
cov_both_ch <- mask(crop(polygon_raster, desert_both_raster), desert_both_raster) 
  
area_both_ch <- as.data.frame(cov_both_ch, na.rm = TRUE) %>%
      tally() %>%
      mutate(area = n * res(cov_both_ch)[1] * res(cov_both_ch)[2]) %>% 
      dplyr::select(area)

#area_pol_biome <- sum(unlist(area_biome_ch))

area_both_ch$area / area_both$area

# 0.4983129 (of both areas covered)
```



## Area per region
```{r}
polygon_region <- polygons_data %>% 
  st_make_valid() %>% 
  group_by(contnnt) %>% 
  summarize() %>% 
  st_make_valid()

polygon_region$area <- st_area(polygon_region$geometry)
area_sum <- sum(polygon_region$area)

polygon_region$perc <- polygon_region$area / area_sum
```


## Region area of earth's surface
```{r}
polygon_region$reg.perc.earth <- sapply(polygon_region$area, function(x) {x / 1.5e+14})
```


# Plotting



## Aridity, Biome and Checklists
```{r}
ggplot()+
  geom_sf(aes(fill = "Biome"), data = biome_only_sf$geometry, col = "transparent") +
  geom_sf(aes(fill = "Aridity"), data = arid_only_sf$geometry, col = "transparent")+
  geom_sf(aes(fill = "Overlap"), data = desert_both$geometry, col = "transparent")+
  scale_fill_manual(values = c("#1B9E77", "#7570B3", "#D95F02")) +
  geom_sf(data = world_coast, col = "grey70", size = 0.3) +
  geom_sf(data = polygons_data, aes(geometry = geometry, color = "Checklists"), size = 0.75, fill = "transparent") +
  scale_color_manual(values = c(Checklists = "grey30")) +
  theme_bw() +
  labs(fill = "Desert definition", color = "") +
  theme(axis.title = element_text(size = 12),
        panel.border = element_blank(),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 12),
        legend.position = "bottom") +
  coord_sf(crs = "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs")
```

```{r}
ggsave("figure1.png", last_plot(), device = "png", path = here::here("./data/results/"), width = 20, height = 12, units = "cm")
```


## Checklists as assigned to main regions

### Preparation of island checklists
```{r}
# determine centroids of islands for plotting
islands <- polygons_data %>% 
  filter(islnd_m == "Island") %>% 
  st_centroid()
```

### Summarize checklist shapefile per region
```{r}
region.shp <- polygons_data %>% 
  st_make_valid() %>% 
  group_by(contnnt) %>% 
  summarize()
```

### Color scale for plotting
```{r}
col.islands <- scales::brewer_pal("qual", palette = "Dark2")
col.islands(6)
col.islands <- c("#1B9E77", "#D95F02", "#7570B3", "#66A61E", "#E6AB02")
col.cont <- c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E", "#E6AB02")

```

### Plotting
```{r}
ggplot()+
  geom_sf(data = world_coast, col = "grey30", size = 0.3) +
  geom_sf(data = region.shp, aes(geometry = geometry, fill = contnnt), alpha = 0.5) +
  geom_sf(data = polygons_data, aes(geometry = geometry, col = contnnt), size = 0.6, fill = "transparent") +
  geom_sf(data = islands, aes(col = contnnt), shape = 1, stroke = 1.5, size = 2.5, show.legend = FALSE) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme_bw() +
  theme(axis.title = element_blank(),
        panel.border = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        legend.position = "bottom") +
  coord_sf(crs = "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs")
```


```{r}
ggsave("checklist.regions.png", last_plot(), device = "png", path = here::here("./data/results/"), width = 20, height = 12, units = "cm")
```


## Checklists whether already in GIFT or NEW

```{r}
env_pred_dataset <- read.csv(here::here("./data/analysis/env_pred_dataset.csv"), row.names = 1)
```

```{r}
env_pred_dataset_2 <- env_pred_dataset %>% 
  rownames_to_column(var = "desert")

old_new <- merge(env_pred_dataset_2, polygons_data, by = "desert") %>% 
  st_as_sf()
```

```{r}
ggplot()+
  geom_sf(data = world_coast, col = "grey30", size = 0.3) +
  geom_sf(data = desert_biomes, aes(fill = "Desert areas"), col = "transparent",  size = 0) +
  geom_sf(data = arid_sf, aes(fill = "Desert areas"), col = "transparent",  size = 0) +
  geom_sf(data = old_new, aes(geometry = geometry, fill = category), col = "transparent") +
  scale_fill_manual(values = c("GIFT" = "blue", "New" = "red", "Desert areas" = "grey70"), labels = c("GIFT", "New", "Desert areas")) +
  #scale_fill_brewer(palette = "Set1", direction = -1) +
  theme_bw() +
  theme(axis.title = element_blank(),
        panel.border = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        legend.position = "bottom") +
  coord_sf(crs = "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs")
```

```{r}
ggsave("old.new.png", last_plot(), device = "png", path = here::here("./data/results/"), width = 20, height = 12, units = "cm")
```
