---
title: "SpeciesDiversity_Composition"
author: "Johanna Klapper"
date: "6/1/2022"
output: html_document
---

This Markdown contains:
- Species dataset preparation
- Analysis of endemic/generalist species
- Species richness/area-weighted species richness
- NMDS Analysis


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load packages
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(vegan)
library(sf)
library(sp)
library(reshape2)
library(seriation)
library(rnaturalearth)
library(rnaturalearthdata)
library(kableExtra)
```



# Load data
```{r}
# gift dataset
gift_species <- readRDS(here::here("./data/analysis/20220524_GIFT_desert_checklist.rds"))
gift_desert_perc <- readRDS(here::here("./data/analysis/20220524_GIFT_desert_envpred.rds")) # percentage of area covered by desert per checklist

# non-gift dataset
check_species <- read.csv(here::here("./data/checklists/processed/dataset_proc.csv"))

# checklist polygons
polygons_data <- read_sf(here::here("./data/analysis/polygons_data.shp"))
```


# Species dataset 

## Non-gift dataset
```{r}
# select necessary columns
check_species_short <- check_species %>% 
  dplyr::select(species, native, endemic, desert)
```


## Gift dataset
```{r}
glimpse(gift_species)
```

### Collect entity IDs of checklists that have to be excluded
```{r}
# checklists excluded because not a desert biome (or adjacent biome)
biome_exclude_biome <- gift_desert_perc %>% 
  filter(!biome %in% c("Deserts & Xeric Shrublands", "Mediterranean Forests, Woodlands & Scrub", "Temperate Grasslands, Savannas & Shrublands", "Tropical & Subtropical Grasslands, Savannas & Shrublands", "Montane Grasslands & Shrublands")) %>%
  dplyr::select(entity_ID)

# checklists excluded because percentage of area covered by desert is lower than 70 %
biome_exclude_arid <- gift_desert_perc %>% 
  filter(perc_biome_desert != 0 & perc_biome_desert < 70) %>%  
  dplyr::select(entity_ID)

# alll checklists that have to be excluded
biome_exclude <- bind_rows(biome_exclude_biome, biome_exclude_arid)
```

```{r}
# 'Nullarbor, Australia' exists twice -> rename one Nullarbor, Australia to Nullarbor Australia (2)
gift_species <- gift_species %>% 
  mutate(geo_entity = case_when(list_ID == "14770" ~ "Nullarbor, Australia (2)",
                                 TRUE ~ geo_entity))
```

### Filter gift dataset by entity ID
```{r}
gift_species_short <- gift_species %>% 
  dplyr::select(species, native, end_list, geo_entity, entity_ID) %>% 
  mutate_at("entity_ID", as.numeric) %>% 
  filter(!entity_ID %in% biome_exclude$entity_ID) %>% 
  dplyr::rename(endemic = end_list,
         desert = geo_entity) %>% 
  mutate_at("endemic", as.numeric) %>% 
  dplyr::select(-entity_ID) %>% 
  filter(!desert %in% c("Patos", "Salsipuedes", "Alcatraz")) #no environmental data available for those three areas

length(unique(gift_species_short$desert))
length(unique(gift_species_short$species))
```

## Combine gift and non-gift dataset
```{r}
species_data <- bind_rows(check_species_short, gift_species_short)

glimpse(species_data)
```


## Endemic species
```{r}
# endemic on region scale
species_data_reg <- species_data %>%
  merge(polygons_data, by = "desert") %>% 
  dplyr::select(contnnt, species)


continent <- c("Asia", "North America", "North Africa", "South America", "South Africa", "Oceania")

tempList <- vector("list", length(continent))
tempList.extra <- vector("list", length(continent))
tempList.end <- vector("list", length(continent))


for (i in 1:6) {

  tempList[i] <- species_data_reg %>% 
    filter(contnnt == continent[i]) %>% 
    dplyr::select(species) %>% 
    unique()

  tempList.extra[i] <- species_data_reg %>% 
    filter(contnnt != continent[i]) %>% 
    dplyr::select(species) %>% 
    unique()

  tempList.end[i] <- setdiff(tempList[[i]], tempList.extra[[i]]) %>% as.data.frame()
}



end.species <- unlist(tempList.end) %>% 
  unique() %>% 
  as.data.frame() %>% 
  dplyr::rename(species = '.')

species_data <- species_data %>% 
  mutate(endemic.reg = ifelse(species %in% end.species$species, "endemic", "non-endemic"))
```


## Save species dataset
```{r}
write.csv(species_data, here::here("./data/analysis/species.csv"), row.names = FALSE)
```





# Load data
```{r}
species_data <- read.csv(here::here("./data/analysis/species.csv"))
```

# Some preparation
```{r}
# if species is endemic, add the region they are endemic to
species_data <- species_data %>% 
  merge(polygons_data, by = "desert") %>% 
  mutate(endemic.reg2 = ifelse(endemic.reg == "endemic", contnnt, "non-endemic"))
```

```{r}
# check that there's no checklist missing
setdiff(species_data$desert, polygons_data$desert)
```


# Some general analysis
```{r}
# Number of species in gift dataset
length(unique(gift_species_short$species))

# Number of checklists in gift dataset
length(unique(gift_species_short$entity_ID))

# Number of species in non-gift dataset
length(unique(check_species_short$species))

# Number of checklists in non-gift dataset
length(unique(check_species_short$desert))
```

```{r}
# Number of checklists
length(unique(species_data$desert))

# Number of species total
length(unique(species_data$species))
```


# Analysis of endemic species

## Data preparation
```{r}
spec.data.end <- species_data %>% 
  distinct(species, .keep_all = TRUE) %>% 
  group_by(endemic.reg2) %>% 
  summarise(n = n())

spec.data.end$endemic.reg2 <- factor(spec.data.end$endemic.reg2, levels = c("non-endemic", "North America", "Asia", "South America", "Oceania", "South Africa", "North Africa"), ordered = TRUE)
```

## Color scale
```{r}
col.regions <- scales::brewer_pal("qual", palette = "Dark2")
col.regions(7)

fill.regions <- c("#A6761D", "#7570B3", "#1B9E77", "#E6AB02", "#E7298A", "#66A61E", "#D95F02")
```

## Plotting
```{r}
ggplot(data = spec.data.end, aes(x = endemic.reg2, y = n, fill = endemic.reg2)) +
  geom_segment(aes(xend=endemic.reg2, yend=0), size = 1) +
  geom_point(size=7, aes(color = endemic.reg2)) +
  scale_color_manual(values = fill.regions) +
  scale_x_discrete(labels=c("non-endemic", "North \nAmerica", "Asia", "South \nAmerica", "Oceania", "South \nAfrica", "North \nAfrica")) +
  labs(x = "", y = "Number of (non-)endemic species") +
  theme_bw() +
  theme(axis.title = element_text(size = 17),
        axis.text = element_text(size = 17),
        legend.position = "none")
```

```{r}
ggsave("bar.end.spec.png", last_plot(), device = "png", path = here::here("./data/results/"), width = 27, height = 15, units = "cm")
```

## Endemism statistics
```{r}
# Number of unique species per region
uni.species <- species_data %>% 
  distinct(species, contnnt)

table(uni.species$contnnt)
```

```{r}
# Number of endemic species per region
spec.data.end
```


```{r}
# Percentages of endemic species per region

#Asia
7557/10607

#North Africa
3289/6089

#North America 
12700/13937

#Oceania
5912/6186

#South Africa 
3908/4337

#South America 
6554/7390


#non-endemic
3794/43714
```


```{r}
# Species in at least 4, 5, 6 regions
species_data %>% 
  dplyr::select(species, contnnt) %>% 
  unique() %>%  
  group_by(species) %>% 
  summarise(n = n()) %>% 
  filter(n >= 6)

# 165 species in 4 regions
# 44 species in 5 regions
# 29 species in 6 regions, e.g. Cyperus rotundus, Portulaca oleracea
```


# Diversity analysis

## Presence/absence matrix
```{r}
species_data_bin <- species_data %>% 
  dplyr::select(species, desert) %>% 
  mutate(count = 1) %>% 
  unique() %>% 
  pivot_wider(names_from=species,values_from = count,values_fill = 0,) %>% 
  as.data.frame()

rownames(species_data_bin) <- species_data_bin$desert

species_matrix <- species_data_bin %>% dplyr::select(-desert) 
```

```{r}
head(rowSums(species_matrix))
```

```{r}
head(sort(rowSums(species_matrix), decreasing = TRUE))
```

```{r}
head(sort(rowSums(species_matrix), decreasing = FALSE))
```

```{r}
summary(rowSums(species_matrix))
```

```{r}
hist(rowSums(species_matrix),
     col = "grey", # plot title
     main = "",
     xlab = "Number of species") # x-axis title
```



## Distribution of species/area across the globe

### Species number per checklist (and per km2)
```{r}
# Environmental dataset for area information
env_pred_dataset <- read.csv(here::here("./data/analysis/env_pred_dataset.csv"), row.names = 1)


spec_num <- rowSums(species_matrix) %>% 
  as.data.frame() %>% 
  rownames_to_column() %>% 
  dplyr::rename(desert = rowname,
                spec = '.')

area_geodis <- env_pred_dataset %>% 
  rownames_to_column() %>% 
  dplyr::rename(desert = rowname) %>% 
  dplyr::select(desert, Area)

spec_geodis <- merge(spec_num, area_geodis, by = "desert") %>% 
  mutate(spec_area = spec / Area * 1000000) # spec per km2

spec_geodis <- merge(spec_geodis, unique(polygons_data), by = "desert") %>% 
  distinct(desert, .keep_all = TRUE)
```

### Centroid of each checklists for plotting
```{r}
# Coastlines of the world
world_coast <- ne_coastline(scale = "medium", returnclass = "sf")

# some polygons are multipolygons -> not possible to get centroid
no_multi_poly <- st_cast(st_make_valid(polygons_data), "POLYGON") %>% 
  distinct(desert, .keep_all = TRUE) 

# centroids of polygons
plots_cent <- geosphere::centroid(as_Spatial(no_multi_poly$geometry)) %>% 
  as.data.frame() %>% 
  st_as_sf(coords = c("V1","V2"), crs = st_crs(world_coast))

plots_cent <- st_join(plots_cent, no_multi_poly, join = st_intersects) 

# join with species data
spec_geodis_sf <- merge(spec_geodis, plots_cent, by = "desert") %>% 
  dplyr::select(-geometry.x) %>% 
  st_as_sf() %>% 
  distinct(desert, .keep_all = TRUE)
```

### Plotting
```{r}
spec_dis_plot <- ggplot()+
  geom_sf(data = world_coast, size = 0.3) +
  geom_sf(data = spec_geodis_sf, aes(fill = spec), size = 5.5, shape = 21, col = "transparent", alpha = 0.8) +
    #scale_size_continuous(name="Absolute Species Number", range=c(1,7), breaks=my.breaks) +
    #scale_alpha_continuous(name="Absolute Species Number", range=c(0.2, 1), breaks=my.breaks) +
    #scale_color_gradient(low = "darkgreen", high = "darkgreen", breaks = my.breaks, name="Absolute Species Number") +
    #scale_fill_gradient(low = "darkgreen", high = "darkgreen", breaks = my.breaks, name="Absolute Species Number", guide = guide_legend(override.aes = list(alpha = 1)) ) +
    #scale_color_continuous(type = "viridis", name = "Species per km2") +
  scale_fill_viridis_c(name="Species number per checklist", option = "D", breaks = c(500, 2000,4000)) +
  theme_bw() +
  theme(
      legend.position = c("bottom"),
      panel.border = element_rect(fill = NA, colour = NA),
      axis.title = element_blank(),
      legend.text = element_text(size = 13, angle = 0),
      legend.title = element_text(size = 13),
      legend.key.size = unit(0.8, 'cm'),
      legend.key.width = unit(1, 'cm')) +
  guides(fill=guide_colorbar(ticks.colour = NA)) +
  #guides(color = guide_legend(ncol=2), size = guide_legend(ncol = 2), shape = guide_legend(ncol = 2), alpha = guide_legend(ncol = 2)) +
  coord_sf(crs = "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs")

spec_dis_plot
```


```{r}
ggsave("species.distribution.png", spec_dis_plot, device = "png", path = here::here("./data/results/"), width = 20, height = 12, units = "cm")
```


## Histogram of species richness distribution
```{r}
hist.1 <- ggplot(data = spec_geodis) +
  geom_histogram(aes(x = spec), fill = "darkgreen", col = "black", alpha = 0.7) +
  theme_classic() +
  labs(x = "Absolute species numbers per plot", y = "Count")

hist.2 <- ggplot(data = spec_geodis) +
  geom_histogram(aes(x = log(spec +1)), fill = "darkgreen", col = "black", alpha = 0.7) +
  theme_classic() +
  labs(x = "Absolute species numbers per plot (log-transformed)", y = "Count")

hist.12 <- cowplot::plot_grid(hist.1, hist.2, labels = "AUTO", ncol = 2)
ggsave("hist.specrich.png", hist.12, device = "png", path = here::here("./data/results/"), width = 30, height = 15, units = "cm")
```


## Species richness per region

### Data preparation
```{r}
# Species number per region
spec_num_reg <- species_data %>% 
  group_by(contnnt) %>% 
  distinct(species, .keep_all = TRUE) %>% 
  summarize(sum = n()) %>% 
  as.data.frame()
```

```{r}
# one polygon for each region 
poly_region <- polygons_data %>% 
  st_make_valid() %>% 
  group_by(contnnt) %>% 
  summarize()

# merge with species data
spec.rich.region <- spec_num_reg %>% 
  merge(poly_region, by = "contnnt") %>% 
  st_as_sf()

# calculate area-weighted species richness
spec.rich.region$area <- st_area(st_make_valid(spec.rich.region$geometry))
spec.rich.region$spec.area <- spec.rich.region$sum / spec.rich.region$area *1000000
```


### Plotting
```{r}
# order regions by species richness
spec.rich.region$spec.area <- spec.rich.region$spec.area %>%
  units::drop_units() 
spec.rich.region <- spec.rich.region %>% 
  arrange(spec.area, decreasing = FALSE)
```

#### Barplot of area-weighted species richness per region
```{r}
ggplot(data = spec.rich.region, aes(x = fct_inorder(contnnt), y = spec.area)) +
  #geom_col() +
  geom_segment(aes(xend=contnnt, yend=0), size = 1) +
  geom_point(size=7, aes(color = contnnt)) +
  scale_color_brewer(palette = "Dark2") +
  theme_bw() +
  theme(axis.title = element_text(size = 19),
        axis.text = element_text(size = 16),
        legend.position = "none") +
  labs(x = "", y = bquote("Species/area [" ~ m^-2 ~"]"))
```

```{r}
ggsave("species.richness.png", last_plot(), device = "png", path = here::here("./data/results/"), width = 29, height = 20, units = "cm")
```


#### Map plotting of species richness
```{r}
# Color scale
cols.rich.pal <- scales::brewer_pal("seq", "Greens")(7)
col.pal <- scales::gradient_n_pal(cols.rich.pal) (seq(0.2,1, length.out = 7))
cols.rich <- c("#9df100", "#82cd00", "#67aa00", "#4e8801", "#366801", "#1f4a01", "#092d01")
```


```{r}
ggplot()+
  geom_sf(data = world_coast, size = 0.3) +
  geom_sf(data = spec.rich.region, aes(fill = contnnt), col = "transparent") +
    scale_fill_manual(name="Species numbers \nper region", values = c("North America" = cols.rich[7], "Asia" = cols.rich[6], "South America" = cols.rich[5], "Oceania" = cols.rich[4], "North Africa" = cols.rich[3], "South Africa" = cols.rich[2]), labels = c("13937 (NAm)", "10607 (A)" , "7390 (SAm)", "6186 (O)", "6089 (NAf)", "4337 (SAf)")) +
  theme_bw() +
  theme(
      legend.position = "bottom",
      panel.border = element_rect(fill = NA, colour = NA),
      axis.title = element_blank(),
      legend.text = element_text(size = 12),
      legend.title = element_text(size = 12)) +
  guides(color = guide_legend(ncol=2), size = guide_legend(ncol = 2), shape = guide_legend(ncol = 2),
         alpha = guide_legend(override.aes = list(alpha = 1))) +
  coord_sf(crs = "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs")
```

```{r}
ggsave("species.richness.region.png", last_plot(), device = "png", path = here::here("./data/results/"), width = 20, height = 12, units = "cm")
```




# NMDS Analysis

## Stress values for different n of dimensions
```{r}
n <- 12
stress <- vector(length = n)
for (i in 1:n) {
    stress[i] <- metaMDS(species_matrix, distance = "chao", k = i)$stress
}

names(stress) <- paste(1:n, "Dim", sep = " ")
stress <- as.data.frame(stress) %>% 
  rownames_to_column(var = "Dimensions")

nmds.stress <- ggplot(data = stress, aes(x = fct_inorder(Dimensions), y = stress)) +
  geom_col() +
  labs(x = "NMDS Dimensions", y = "Stress") +
  theme_bw() +
  theme(rect = element_rect(size = 0.2))
nmds.stress
```

```{r}
ggsave("nmds.stress.png", nmds.stress, device = "png", path = here::here("./data/results/"), width = 20, height = 12, units = "cm")
```


## Run NMDS
```{r}
spec.NMDS <- metaMDS(species_matrix, k = 12, distance = "chao")

spec.NMDS$stress
```


## Retrieving data from NMDS
```{r}
spec.NMDS.species <- as.data.frame(spec.NMDS$species)  
spec.NMDS.species$species <- rownames(spec.NMDS.species) # column with species names
spec.NMDS.species <- merge(spec.NMDS.species, species_data, by = "species", all.y = FALSE) %>%  # add information about endemism
  dplyr::select(-c(native, desert)) %>% 
  distinct(species, .keep_all = TRUE)

spec.NMDS.sites <- as.data.frame(spec.NMDS$points)
spec.NMDS.sites$site <- rownames(spec.NMDS.sites)  # create a column of site names, from the rownames of NMDS.scores

spec.NMDS.sites.con <- merge(spec.NMDS.sites, unique(polygons_data), by.x = "site", by.y = "desert") # add information about region, desert definition, etc.
```


### Shepard diagram
```{r}
# Create a tibble that contains the data from stressplot
shepard.df <- tibble(x = stressplot(spec.NMDS)$x,
       y = stressplot(spec.NMDS)$y,
       yf = stressplot(spec.NMDS)$yf) %>%
  # Change data to long format
  pivot_longer(cols = c(y, yf),
               names_to = "var")

# Create plot
shepard.df %>%
  ggplot(aes(x = x, y = value)) +
  # Add points just for y values
  geom_point(data = shepard.df %>% filter(var == "y"), pch = 1, alpha = 0.5, size = 2) +
  # Add line just for yf values
  geom_step(data = shepard.df %>%
              filter(var == "yf"),
            col = "red",
            direction = "vh", size = 1) +
  # Add correlation statistics
  geom_text(aes(x = 0.25, y = 1.6, label = "Non-metric fit, R-squared = 1
       Linear fit,         R-squared = 0.993", family = "sans"), col = "black", size = 6) +
  # Change axis labels
  labs(x = "Observed Dissimilarity", y = "Ordination Distance") +
  # Add bw theme
  theme_bw() +
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 11))
```

```{r}
ggsave("nmds.shepard.png", last_plot(), device = "png", path = here::here("./data/results/"), width = 20, height = 12, units = "cm")
```


### NMDS Plot

#### Checklists colored for regions
```{r}
fig.31 <- ggplot() +
  geom_point(data = spec.NMDS.species, aes(x = MDS1, y = MDS2), pch = 1, alpha = 0.3, size = 2.5, stroke = 1.1) +
  geom_point(data = spec.NMDS.sites.con, aes(x = MDS1, y = MDS2, fill = contnnt), pch = 24, size = 3.5, col = "transparent") +
  scale_fill_brewer(palette = "Dark2") +
  labs(fill = "Region", x = "NMDS 1", y = "NMDS 2") +
  theme_bw() +
  theme(legend.title = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.position = c(0.25, 0.15),
        legend.box.background = element_rect(colour = "black"),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 13)) +
  guides(fill=guide_legend(ncol=2, keywidth = 0.6, keyheight = 0.6))
```


#### Species colored for region they are endemic to
```{r}
# color scale
col.fun <- scales::brewer_pal("qual", "Dark2")
col.fun(6)
cols.end <- c("black", "#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E", "#E6AB02")

# labels
labels.end <- c("Asia", "North America", "North Africa", "South America", "South Africa", "Oceania")

# plotting  
fig.32 <- ggplot() +
  geom_point(data = spec.NMDS.species %>% filter(endemic.reg2 == "non-endemic"), aes(x = MDS1, y = MDS2, col = "black"), pch = 1, size = 3, alpha = 0.4, stroke = 1.1) +
  scale_color_manual(values = "black", labels = "non-endemic", guide = guide_legend(override.aes = list(alpha = 1))) +
  geom_point(data = spec.NMDS.species %>% filter(endemic.reg2 != "non-endemic"), aes(x = MDS1, y = MDS2, fill = as.character(endemic.reg2)), pch = 21, size = 3.5, alpha = 0.9, col = "transparent") +
  scale_fill_brewer(palette = "Dark2", guide = guide_legend(override.aes = list(alpha = 1)), breaks = labels.end) +
  labs(x = "NMDS 1", y = "NMDS 2", fill = "endemic in", col = "") +
  theme_bw() +
  theme(legend.text = element_text(size = 15),
        legend.position = c(0.77, 0.13),
        legend.box.background = element_rect(colour = "black"),
        legend.spacing.y = unit(0.01, 'cm'),
        legend.key.size = unit(0.4, "cm"),
        legend.title = element_text(size = 15),
        legend.margin = margin(t = 0.04, unit='cm'),
        legend.box.margin = margin(t = 0.04, unit='cm'),
        axis.text = element_text(size = 14)) +
  guides(fill=guide_legend(ncol=2, keywidth = 0.6, keyheight = 0.6))
fig.32
```


#### Checklists colored for region and mainland/island
```{r}
fig.33 <- ggplot(spec.NMDS.sites.con) +
  geom_point(data = spec.NMDS.species, aes(x = MDS1, y = MDS2), pch = 1, stroke = 1.1, size = 4, alpha = 0.2, col = "grey20") +
  geom_point(data = spec.NMDS.sites.con, aes(x = MDS1, y = MDS2, fill = contnnt, col = contnnt, shape = islnd_m), size = 3.5, stroke = 1.3) +
  #scale_fill_manual(values = c("darkorange", "darkolivegreen"), guide = guide_legend(override.aes = list(alpha = 1))) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  scale_shape_manual(values = c(2, 24)) +
  labs(x = "NMDS 1", y = "NMDS 2", fill = "Region", col = "Region") +
  theme_bw() +
  theme(legend.title = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.position = c(0.23, 0.12),
        legend.box.background = element_rect(colour = "black"),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 13)) +
  guides(fill=guide_legend(ncol=2, keywidth = 0.6, keyheight = 0.9, override.aes=list(shape = 24)), shape = "none")
fig.33
```


#### Checklists colored for desert definition
```{r}
fig.34 <- ggplot() +
  geom_point(data = spec.NMDS.species, aes(x = MDS1, y = MDS2), pch = 1, alpha = 0.3, size = 2.5, stroke = 1.1) +
  geom_point(data = spec.NMDS.sites.con, aes(x = MDS1, y = MDS2, fill = dsrt_bt), pch = 24, size = 4.5, col = "transparent") +
  scale_fill_manual(values = c( "#D95F02", "#1B9E77", "#7570B3"), labels = c("Overlap", "Aridity", "Biome")) +
  labs(fill = "Desert definition", x = "NMDS 1", y = "NMDS 2") +
  theme_bw() +
  theme(legend.title = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.position = c(0.20, 0.11),
        legend.box.background = element_rect(colour = "black"),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 13)) +
  guides(fill=guide_legend(ncol=2, keywidth = 0.6, keyheight = 1))
fig.34
```


#### Save plots
```{r}
ggsave("figure3a.png", fig.31, device = "png", path = here::here("./data/results/"), width = 22, height = 15, units = "cm")
ggsave("figure3b.png", fig.32, device = "png", path = here::here("./data/results/"), width = 22, height = 15, units = "cm")
ggsave("figure3c.png", fig.33, device = "png", path = here::here("./data/results/"), width = 22, height = 15, units = "cm")
ggsave("figure3d.png", fig.34, device = "png", path = here::here("./data/results/"), width = 22, height = 15, units = "cm")
```
