---
title: "EnvironmentalDistance"
author: "Johanna Klapper"
date: "5/23/2022"
output: html_document
---

This Markdown contains:
- pairwise correlation of environmental predictors
- PCA Analysis
- Plotting of PCs on PCA space
- Plotting of PCs on map
- Anova for regions
- Boxplots of predictors


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(vegan)
library(FactoMineR)
library(GGally)
library(ggrepel)
library(ggforce)
library(tidyquant)
library(reshape)
library(ggExtra)
library(sf)
library(kableExtra)
library(rnaturalearth)
library(rnaturalearthdata)
```


# Load data
```{r}
env_pred_dataset <- read.csv(here::here("./data/analysis/env_pred_dataset.csv"), row.names = 1)
```


# Selecting necessary columns and remove NAs
```{r}
env_pred_analysis <- env_pred_dataset %>% 
  dplyr::select(-c(category, seasT_sd, seasP_sd, Alt_sd, TRI_sd)) %>% 
  drop_na() 
```


# Correlation and distribution of variables

## Non-transformed variables
```{r}
ggpairs(env_pred_analysis, upper = list(continuous = wrap(ggally_cor, digits=2)))
```

```{r}
# Distribution of area as one example of a skewed distribution
area <- env_pred_analysis %>% 
  mutate(area = Area/1000000) %>% 
  mutate(area = as.double(area))
  

ggplot(data = area) +
  geom_histogram(aes(x = as.double(area)), size = 1.5, bins = 50) +
  theme_bw() +
  labs(y = "Count", x = bquote("Area [" ~ km^2 ~ "]")) +
  theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 15))

ggsave("area.density.png", last_plot(), device = "png", path = here::here("./data/results/"), width = 25, height = 14, units = "cm")
```


## Transformation
```{r}
# Determine how to transform SLMP
hist(model_data$SLMP)
hist(log(model_data$SLMP))
hist(sqrt(model_data$SLMP))
hist(log10(max(model_data$SLMP+1) - model_data$SLMP))
slmp <- car::powerTransform(model_data$SLMP+1)
summary(slmp)

hist(model_data$SLMP^2.1)
```

```{r}
env_pred_analysis_log <- env_pred_analysis 

env_pred_analysis_log[ , 1:11] <- log(env_pred_analysis_log[ , 1:11] +1)
env_pred_analysis_log[ , 12] <- env_pred_analysis_log[ , 12]^2.1
env_pred_analysis_log[ , 13] <- log(env_pred_analysis_log[ , 13] +1)
```


```{r}
pairs <- ggpairs(env_pred_analysis_log, upper = list(continuous = wrap(ggally_cor, digits = 2, size = 6))) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size=9),
        axis.text.y = element_text(size = 9),
        strip.text = element_text(size = 13)) 
pairs
```


```{r}
ggsave("pairsplot.png", pairs, device = "png", path = here::here("./data/results/"), width = 34, height = 29, units = "cm")
```



# PCA Analysis

```{r}
pca.A <- PCA(env_pred_analysis_log, quanti.sup = 1) # Area as supplementary variable
```


## Plotting preparation
```{r}
# join checklist and environmental data
polygons_data <- read_sf(here::here("./data/analysis/polygons_data.shp"))

env_pred_dataset_na <- env_pred_dataset %>% 
  drop_na() %>% 
  rownames_to_column()

pca_poly_data <- polygons_data %>% 
  st_drop_geometry() %>% 
  filter(desert %in% env_pred_dataset_na$rowname) %>% 
  distinct(desert, .keep_all = TRUE) 

setdiff(rownames(env_pred_analysis), pca_poly_data$desert)
```


```{r}
# extract pc scores for first three component and add to dataframe
pca.plot.A <- data.frame(rep(NA, 163))
pca.plot.A$pc1 <- pca.A$ind$coord[, 1] # indexing the first column
pca.plot.A$pc2 <- pca.A$ind$coord[, 2]  # indexing the second column
pca.plot.A$pc3 <- pca.A$ind$coord[, 3]  # indexing the third column
pca.plot.A$desert <- names(pca.A$ind$dist)

# join with checklist/environmental data
pca.plot.A <- merge(pca.plot.A, pca_poly_data, by = "desert")

# also need to extract the data for the variable contributions to each of the pc axes.

pca.vars.A <- pca.A$var$coord %>% 
  data.frame
pca.vars.A <- pca.vars.A * 4
pca.vars.A$vars <- rownames(pca.vars.A)
pca.vars.m.A <- melt(pca.vars.A, id.vars = "vars")

# extract data for suplementary variable
pca.vars.sup.A <- pca.A$quanti.sup$coord %>% 
  data.frame
pca.vars.sup.A <- pca.vars.sup.A * 4
pca.vars.sup.A$vars <- rownames(pca.vars.sup.A)
```

```{r}
# labels
label.A <- pca.vars.A$vars
label.sup.A <- pca.vars.sup.A$vars
```

```{r}
# color scale
RColorBrewer::brewer.pal(8, name = "Dark2")
cols.reg <- c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E", "#E6AB02", "#A6761D", "#666666")
cols.def <- c("#D95F02", "#1B9E77", "#7570B3")
```


## Plotting

### Variances explained by axes
```{r}
pca.eig.A <- pca.A$eig[ ,2] %>% 
  as.vector() %>% 
  as.data.frame()

pca.axes.A <- ggplot(data = pca.eig.A, aes(x = fct_inorder(paste0("PC", 1:12), .), y = ., group = FALSE)) +
  geom_point(size = 2) +
  geom_line() +
  labs(x = "PCA axes", y = "Percentage of variance [%]") +
  theme_bw() +
  theme(rect = element_rect(size = 0.2),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 15))
pca.axes.A
```

```{r}
ggsave("pca.axes.A.png", pca.axes.A, device = "png", path = here::here("./data/results/"), width = 20, height = 12, units = "cm")
```



### Colored in for regions
```{r}
# First and second principal component
fig.A1 <- ggplot() +
  geom_point(data = pca.plot.A, aes(x = pc1, y = pc2, fill = contnnt, col = contnnt, shape = islnd_m), size = 3.5, stroke = 1.5) +
  scale_fill_manual(values = cols.reg) +
  scale_color_manual(values = cols.reg) +
  scale_shape_manual(values = c(1, 21)) +
  geom_segment(data = pca.vars.A, aes(x = 0, y = 0, xend = Dim.1, yend = Dim.2), size = 1, col = "black", arrow = arrow(length = unit(0.3,"cm"))) +
  geom_text(aes(x = Dim.1*1.2, y = Dim.2*1.2, label = label.A), data = pca.vars.A, check_overlap = FALSE, col = "black", size = 6.5) +
  geom_segment(data = pca.vars.sup.A, aes(x = 0, y = 0, xend = Dim.1, yend = Dim.2), size = 1, col = "blue",  arrow = arrow(length = unit(0.3,"cm"))) +
  geom_text(aes(x = Dim.1*1.1, y = Dim.2*2.1, label = label.sup.A), data = pca.vars.sup.A, check_overlap = TRUE, col = "blue", size = 6.5) +
  theme_bw() +
  theme(legend.title = element_text(size = 17),
        legend.text = element_text(size = 17),
        legend.position = c(0.21, 0.11),
        legend.box.background = element_rect(colour = "black"),
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 14))+
  labs(x = "PC 1 (37.48%)", y = "PC 2 (21.36%)", fill = "Region", col = "Region")+
  guides(fill=guide_legend(ncol=2, keywidth = 0.6, keyheight = 0.6), shape = "none") +
  xlim(-6, 5)

fig.A <- ggMarginal(fig.A1, groupFill = TRUE, groupColour = TRUE) # adding density curves
fig.A
```

```{r}
ggsave("figure.pca.A.png", fig.A, device = "png", path = here::here("./data/results/"), width = 31, height = 22, units = "cm")
```



```{r}
# First and third principal component (not included in thesis)
fig.A2 <- ggplot() +
  geom_point(data = pca.plot.A, aes(x = pc1, y = pc3, fill = contnnt, col = contnnt), pch = 21, size = 3.5) +
  scale_fill_manual(values = cols.reg) +
  scale_color_manual(values = cols.reg) +
  #scale_fill_brewer(palette = "Dark2", direction = 1) +
  #scale_color_brewer(palette = "Dark2", direction = 1) +
  geom_segment(data = pca.vars.A, aes(x = 0, y = 0, xend = Dim.1, yend = Dim.3), size = 1, col = "black", arrow = arrow(length = unit(0.3,"cm"))) +
  geom_text(aes(x = Dim.1*1.2, y = Dim.3*1.2, label = label.A), data = pca.vars.A, check_overlap = FALSE, col = "black", size = 6) +
  geom_segment(data = pca.vars.sup.A, aes(x = 0, y = 0, xend = Dim.1, yend = Dim.3), size = 1, col = "blue", linetype = "dashed",  arrow = arrow(length = unit(0.3,"cm"))) +
  geom_text(aes(x = Dim.1*1.2, y = Dim.3*1.2, label = label.sup.A), data = pca.vars.sup.A, check_overlap = TRUE, col = "blue", size = 6) +
  theme_bw() +
  theme(legend.title = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.position = c(0.17, 0.09),
        legend.box.background = element_rect(colour = "black"),
        axis.title = element_text(size = 16))+
  labs(x = "PC 1 (37.2%)", y = "PC 3 (13.4%)", fill = "Region", col = "Region")+
  guides(fill=guide_legend(ncol=2, keywidth = 0.6, keyheight = 0.6)) +
  xlim(-6, 5)

# Second and third principal component (not included in thesis)
fig.A3 <- ggplot() +
  geom_point(data = pca.plot.A, aes(x = pc2, y = pc3, fill = contnnt, col = contnnt), pch = 21, size = 3.5) +
  scale_fill_manual(values = cols.reg) +
  scale_color_manual(values = cols.reg) +
  #scale_fill_brewer(palette = "Dark2", direction = 1) +
  #scale_color_brewer(palette = "Dark2", direction = 1) +
  geom_segment(data = pca.vars.A, aes(x = 0, y = 0, xend = Dim.2, yend = Dim.3), size = 1, col = "black", arrow = arrow(length = unit(0.3,"cm"))) +
  geom_text(aes(x = Dim.2*1.2, y = Dim.3*1.2, label = label.A), data = pca.vars.A, check_overlap = FALSE, col = "black", size = 6) +
  geom_segment(data = pca.vars.sup.A, aes(x = 0, y = 0, xend = Dim.2, yend = Dim.3), size = 1, col = "blue", linetype = "dashed",  arrow = arrow(length = unit(0.3,"cm"))) +
  geom_text(aes(x = Dim.2*1.2, y = Dim.3*1.2, label = label.sup.A), data = pca.vars.sup.A, check_overlap = TRUE, col = "blue", size = 6) +
  theme_bw() +
  theme(legend.title = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.position = c(0.17, 0.09),
        legend.box.background = element_rect(colour = "black"),
        axis.title = element_text(size = 16))+
  labs(x = "PC 2 (16.3%)", y = "PC 3 (13.4%)", fill = "Region", col = "Region")+
  guides(fill=guide_legend(ncol=2, keywidth = 0.6, keyheight = 0.6)) +
  xlim(-6, 5)
```

```{r}
ggsave("figure.pcaB.png", fig.A2, device = "png", path = here::here("./data/results/"), width = 29, height = 17, units = "cm")
ggsave("figure.pcaC.png", fig.A3, device = "png", path = here::here("./data/results/"), width = 29, height = 17, units = "cm")
```



### Colored in for desert definition
```{r}
pca.desert.a <- ggplot() +
  geom_point(data = pca.plot.A, aes(x = pc1, y = pc2, fill = dsrt_bt, col = dsrt_bt, shape = islnd_m), stroke = 1.5, size = 3.5) +
  scale_fill_manual(values = cols.def, labels = c("Overlap", "Aridity", "Biome")) +
  scale_color_manual(values = cols.def, labels = c("Overlap", "Aridity", "Biome")) +
  scale_shape_manual(values = c(1, 21)) +
  #scale_fill_brewer(palette = "Dark2", direction = 1) +
  #scale_color_brewer(palette = "Dark2", direction = 1) +
  geom_segment(data = pca.vars.A, aes(x = 0, y = 0, xend = Dim.1, yend = Dim.2), size = 1, col = "black", arrow = arrow(length = unit(0.3,"cm"))) +
  geom_text(aes(x = Dim.1*1.15, y = Dim.2*1.15, label = label.A), data = pca.vars.A, check_overlap = FALSE, col = "black", size = 7) +
  geom_segment(data = pca.vars.sup.A, aes(x = 0, y = 0, xend = Dim.1, yend = Dim.2), size = 1, col = "blue",   arrow = arrow(length = unit(0.3,"cm"))) +
  geom_text(aes(x = Dim.1*1.1, y = Dim.2*3.1, label = label.sup.A), data = pca.vars.sup.A, check_overlap = TRUE, col = "blue", size = 7) +
  theme_bw() +
  theme(legend.title = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.position = c(0.19, 0.1),
        legend.box.background = element_rect(colour = "black"),
        axis.title = element_text(size = 16),
        axis.text = element_text(size = 14))+
  labs(x = "PC 1 (37.48%)", y = "PC 2 (21.36%)", fill = "Desert definition", col = "Desert definition")+
  guides(fill=guide_legend(ncol=2, keywidth = 0.6, keyheight = 0.8), shape = "none")

pca.desert <- ggMarginal(pca.desert.a, groupFill = TRUE, groupColour = TRUE)
pca.desert
```

```{r}
ggsave("pca.desert.def.png", pca.desert, device = "png", path = here::here("./data/results/"), width = 29, height = 20, units = "cm")
```



### Plotted on geographical location
```{r}
# Coastlines of the world
world_coast <- ne_coastline(scale = "medium", returnclass = "sf")


# Centroides of polygons
no_multi_poly <- st_cast(st_make_valid(polygons_data), "POLYGON") %>%  # turn multipolygons into polygons
  distinct(desert, .keep_all = TRUE) 

plots_cent <- geosphere::centroid(as_Spatial(no_multi_poly$geometry)) %>%  # get centroid for each polygon
  as.data.frame() %>% 
  st_as_sf(coords = c("V1","V2"), crs = st_crs(world_coast))

plots_cent <- st_join(plots_cent, no_multi_poly, join = st_within) 

pca.geo.data <- merge(plots_cent, pca.plot.A, by = "desert")  # join centroid information with pca data
```

```{r}
# Plotting PC1
pca.geo <- ggplot()+
  geom_sf(data = world_coast, size = 0.3) +
  geom_sf(data = pca.geo.data, aes(fill = pc1), shape = 21, col = "transparent", stroke = 0.7, alpha = 0.7, size = 4) +
    scale_fill_viridis_c(direction = -1, name="PC 1") +
    theme_void() + 
  theme_bw() +
  theme(
      legend.position = "bottom",
      panel.border = element_rect(fill = NA, colour = NA),
      axis.title = element_blank(),
      legend.text = element_text(size = 12),
      legend.title = element_text(size = 13),
      legend.key.size = unit(0.6, "cm"),
      legend.key.width = unit(0.8, "cm")) +
  guides(fill=guide_colorbar(ticks.colour = NA))+
  coord_sf(crs = "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs")

pca.geo
```

```{r}
ggsave("pca.geo.png", pca.geo, device = "png", path = here::here("./data/results/"), width = 20, height = 12, units = "cm")
```


```{r}
# Plotting PC2
pca.geo.2 <- ggplot()+
  geom_sf(data = world_coast, size = 0.3) +
  geom_sf(data = pca.geo.data, aes(fill = pc2), shape = 21, col = "transparent", stroke = 0.7, alpha = 0.7, size = 4) +
    scale_fill_viridis_c(direction = -1, name="PC 2") +
    theme_void() + 
  theme_bw() +
  theme(
      legend.position = "bottom",
      panel.border = element_rect(fill = NA, colour = NA),
      axis.title = element_blank(),
      legend.text = element_text(size = 12),
      legend.title = element_text(size = 13),
      legend.key.size = unit(0.6, "cm"),
      legend.key.width = unit(0.8, "cm")) +
  guides(fill=guide_colorbar(ticks.colour = NA))+
  coord_sf(crs = "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs")

pca.geo.2
```

```{r}
ggsave("pca.geo.2.png", pca.geo.2, device = "png", path = here::here("./data/results/"), width = 20, height = 12, units = "cm")
```



### Anova for regions
```{r}
anova.pc1.A <- aov(pc1 ~ contnnt, data = pca.plot.A)
summary(anova.pc1.A)
anova.pc2.A <- aov(pc2 ~ contnnt, data = pca.plot.A)
summary(anova.pc2.A)
```


#### Tukey multiple pairweise comparisons
```{r}
tukey.1 <- TukeyHSD(anova.pc1.A)

tukey.1.df <- tukey.1$contnnt %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "continent") %>% 
  dplyr::select(continent, diff, 'p adj') %>% 
  mutate(across(where(is.numeric), signif, 2)) %>% 
  dplyr::rename(Region = continent,
                'p-value' = 'p adj')

# add significance information
tukey.1.df <- tukey.1.df %>% 
  mutate(' ' = case_when(tukey.1.df$`p-value` <= 0.001 ~ "***",
                         tukey.1.df$`p-value` <= 0.01 & 'p-value' > 0.001 ~ "**",
                         tukey.1.df$`p-value` <= 0.05 & 'p-value' > 0.01 ~ "*",
                         tukey.1.df$`p-value` <= 0.1 & 'p-value' > 0.05 ~ ".",
                         tukey.1.df$`p-value` <= 1 & 'p-value' > 0.1 ~ "",
                         TRUE ~ ""))
```

```{r}
# significant values in bold
tukey.1.df$`p-value` <- ifelse(
  tukey.1.df$`p-value` < 0.05,
  cell_spec(tukey.1.df$`p-value`, bold = T),
  cell_spec(tukey.1.df$`p-value`, bold = F)
)

# creating table with kableExtra
table_aov1 <- tukey.1.df %>% 
  kable("html", escape = F, digits = 2, table.attr = "style = \"color: black;\"") %>% 
  kable_styling(font_size = 14, html_font = "Cambria", full_width = F, htmltable_class = "lightable-classic-2") %>% 
  add_footnote("Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")

save_kable(table_aov1, file = here::here("./data/results/tableanova.jpg"), self_contained = T, zoom = 3, bs_theme = "flatly") # zoom gives a better resolution
```


```{r}
tukey.2 <- TukeyHSD(anova.pc2.A)

tukey.2.df <- tukey.2$contnnt %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "continent") %>% 
  dplyr::select(continent, diff, 'p adj') %>% 
  mutate(across(where(is.numeric), signif, 2)) %>% 
  dplyr::rename(Region = continent,
                'p-value' = 'p adj')

# add significance information
tukey.2.df <- tukey.2.df %>% 
  mutate(' ' = case_when(tukey.2.df$`p-value` <= 0.001 ~ "***",
                         tukey.2.df$`p-value` <= 0.01 & 'p-value' > 0.001 ~ "**",
                         tukey.2.df$`p-value` <= 0.05 & 'p-value' > 0.01 ~ "*",
                         tukey.2.df$`p-value` <= 0.1 & 'p-value' > 0.05 ~ ".",
                         tukey.2.df$`p-value` <= 1 & 'p-value' > 0.1 ~ "",
                         TRUE ~ ""))
```


```{r}
# significance values in bold
tukey.2.df$`p-value` <- ifelse(
  tukey.2.df$`p-value` < 0.05,
  cell_spec(tukey.2.df$`p-value`, bold = T),
  cell_spec(tukey.2.df$`p-value`, bold = F)
)

# create table with kableExtra
table_aov2 <- tukey.2.df %>% 
  kable("html", escape = F, digits = 2, table.attr = "style = \"color: black;\"") %>% 
  kable_styling(font_size = 14, html_font = "Cambria", full_width = F, htmltable_class = "lightable-classic-2") %>% 
  add_footnote("Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")

save_kable(table_aov2, file = here::here("./data/results/tableanova2.jpg"), self_contained = T, zoom = 3, bs_theme = "flatly") # zoom gives a better resoltuion
```


# Boxplots of predictors

## Looking at predictor distribution across desert definitions
```{r}
env.data.box <- env_pred_analysis %>% 
  rownames_to_column(var = "desert") %>% 
  merge(unique(polygons_data), by = "desert") %>% 
  mutate(desert.def = case_when(dsrt_bt == "desert" ~ "O",
                                dsrt_bt == "desert_arid" ~ "A",
                                dsrt_bt == "desert_biome" ~ "B",
                                TRUE ~ dsrt_bt))

env.predictors <- c("Area", "Temp"  ,  "Temp_sd" ,"seasT"  , "Prec"  ,  "Prec_sd", "seasP" ,  "Alt"  ,   "Range" ,  "TRI"   ,  "Soil" ,  "interP", "SLMP") 
env.predictors.unit <- c(bquote("Area [" ~ m^2 ~ "]"), "Temp [°C]"  ,  "Temp_sd [°C]" ,"seasT [°C]"  , "Prec [mm]"  ,  "Prec_sd [mm]", "seasP [mm]" ,  "Alt [m]"  ,   "Range [m]" ,  "TRI [m]"   ,  "Soil [ ]" ,  "interP [mm]", "SLMP [%]")


box.env.pred <- lapply(1:13, function(i) {
  env.pred <- env.data.box %>% 
    dplyr::select(desert.def, env.predictors[i])

  ggplot() +
    geom_boxplot(data = env.pred, aes(x = desert.def, y = env.pred[, 2], col = desert.def), size = 0.7) +
    scale_color_manual(values = c("#1B9E77",  "#7570B3", "#D95F02")) +
    theme_bw() +
    theme(axis.title = element_text(size = 13),
          axis.text.x = element_text(size = 12),
          legend.position = "none") +
    labs(x = "", y = env.predictors.unit[[i]])

})

box.env.pred[1]
```

```{r}
box.env.plot <- cowplot::plot_grid(box.env.pred[[1]], box.env.pred[[2]], box.env.pred[[3]], box.env.pred[[4]], box.env.pred[[5]], box.env.pred[[6]], box.env.pred[[7]], box.env.pred[[8]], box.env.pred[[9]], box.env.pred[[10]], box.env.pred[[11]], box.env.pred[[12]], box.env.pred[[13]], ncol = 4)

box.env.plot
```


```{r}
ggsave("boxplot.env.def.png", box.env.plot, device = "png", path = here::here("./data/results/"), width = 25, height = 20, units = "cm")
```



## Looking at predictor distribution of island and mainland checklists
```{r}
env.data.box.im <- env_pred_analysis %>% 
  rownames_to_column(var = "desert") %>% 
  merge(unique(polygons_data), by = "desert") 

env.predictors <- c("Area", "Temp"  ,  "Temp_sd" ,"seasT"  , "Prec"  ,  "Prec_sd", "seasP" ,  "Alt"  ,   "Range" ,  "TRI"   ,  "Soil" ,  "interP", "SLMP") 
env.predictors.unit <- c(bquote("Area [" ~ m^2 ~ "]"), "Temp [°C]"  ,  "Temp_sd [°C]" ,"seasT [°C]"  , "Prec [mm]"  ,  "Prec_sd [mm]", "seasP [mm]" ,  "Alt [m]"  ,   "Range [m]" ,  "TRI [m]"   ,  "Soil [ ]" ,  "interP [mm]", "SLMP [%]")


box.env.pred.im <- lapply(1:13, function(i) {
  env.pred <- env.data.box.im %>% 
    dplyr::select(islnd_m, env.predictors[i])

  ggplot() +
    geom_boxplot(data = env.pred, aes(x = islnd_m, y = env.pred[, 2]), size = 0.7) +
    theme_bw() +
    theme(axis.title = element_text(size = 13),
          axis.text.x = element_text(size = 12),
          legend.position = "none") +
    labs(x = "", y = env.predictors.unit[[i]])

})

box.env.pred.im[1]
```

```{r}
box.env.plot.im <- cowplot::plot_grid(box.env.pred.im[[1]], box.env.pred.im[[2]], box.env.pred.im[[3]], box.env.pred.im[[4]], box.env.pred.im[[5]], box.env.pred.im[[6]], box.env.pred.im[[7]], box.env.pred.im[[8]], box.env.pred.im[[9]], box.env.pred.im[[10]], box.env.pred.im[[11]], box.env.pred.im[[12]], box.env.pred.im[[13]], ncol = 4)

box.env.plot.im
```


```{r}
ggsave("boxplot.env.isl.main.png", box.env.plot.im, device = "png", path = here::here("./data/results/"), width = 25, height = 20, units = "cm")
```
