---
title: "AdditionalCode_EnvironmentalPredictors"
author: "Johanna Klapper"
date: "7/29/2022"
output: html_document
---

Additional code: environmental values as already stored in the gift database, but there were unrealistic values, therefore we computed the environmental variables ourselves


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# GIFT dataset

## Load data
```{r}
gift_env <- readRDS(here::here("./data/analysis/20220524_GIFT_desert_envpred.rds"))
gift_entities <- read_sf(here::here("./data/gis_data/geoentities/geoentities_simple.shp"))
gift_elev_range <- readRDS(here::here("./data/analysis/20220525_GIFT_elevrange.rds"))
```

```{r}
glimpse(gift_env)
```

## Prepare data
```{r}
biome_exclude_biome <- gift_env %>% 
  filter(!biome %in% c("Deserts & Xeric Shrublands", "Mediterranean Forests, Woodlands & Scrub", "Temperate Grasslands, Savannas & Shrublands", "Tropical & Subtropical Grasslands, Savannas & Shrublands", "Montane Grasslands & Shrublands")) %>%
  dplyr::select(entity_ID)

biome_exclude_arid <- gift_env %>% 
  filter(biome70 == "<70") %>% 
  dplyr::select(entity_ID)

biome_exclude <- bind_rows(biome_exclude_biome, biome_exclude_arid)

# Tropical & Subtropical Dry Broadleaf Forests
# Temperate Broadleaf & Mixed Forests
```

```{r}
gift_entities_fil <- gift_entities %>% 
  filter(!entt_ID %in% biome_exclude$entity_ID) %>% 
  dplyr::select(entt_ID, ge_ntty)

gift_env_fil <- gift_env %>% 
  inner_join(gift_entities_fil, by = c("entity_ID" = "entt_ID"))

gift_range_area <- gift_elev_range %>% 
  filter(entity_ID %in% gift_env_fil$entity_ID) %>% 
  mutate_at(c("min_mi30_grd", "max_mx30_grd"), as.numeric) %>% 
  mutate(range = max_mx30_grd - min_mi30_grd) %>% 
  dplyr::select(entity_ID, range, area)

gift_env_all <- gift_env_fil %>% 
  merge(gift_range_area, by = "entity_ID")
```


## Which columns are needed?
- entity_ID
- geo_entity
- med_wc2.0_bio_30s_01
- med_wc2.0_bio_30s_04
- med_wc2.0_bio_30s_12
- med_wc2.0_bio_30s_15
- med_mn30_grd
- range
- area
- med_TAXNWRB_1km_ll or med_TAXOUSDA_1km_ll

missing:
- isolation
- age

```{r}
gift_env_desert <- gift_env_all %>% 
  dplyr::select(c(entity_ID, ge_ntty, med_wc2.0_bio_30s_01, med_wc2.0_bio_30s_04, med_wc2.0_bio_30s_12, med_wc2.0_bio_30s_15, med_mn30_grd, range, area, sd_wc2.0_bio_30s_01, sd_wc2.0_bio_30s_04, sd_wc2.0_bio_30s_12, sd_wc2.0_bio_30s_15, sd_mn30_grd, med_mn30_grd_TRI, sd_mn30_grd_TRI))
```


## Adjust column names
```{r}
gift_env_desert_df <- gift_env_desert %>% 
  mutate(across(.cols = c(3:16), as.numeric)) %>% 
  rename(mean_temp_mean = med_wc2.0_bio_30s_01,
         mean_temp_sd = sd_wc2.0_bio_30s_01,
         temp_seas_mean = med_wc2.0_bio_30s_04,
         temp_seas_sd = sd_wc2.0_bio_30s_04,
         mean_prec_mean = med_wc2.0_bio_30s_12,
         mean_prec_sd = sd_wc2.0_bio_30s_12,
         prec_seas_mean = med_wc2.0_bio_30s_15,
         prec_seas_sd = sd_wc2.0_bio_30s_15,
         mean_alt_mean = med_mn30_grd,
         mean_alt_sd = sd_mn30_grd,
         mean_tri_mean = med_mn30_grd_TRI,
         mean_tri_sd = sd_mn30_grd_TRI) %>% 
  dplyr::select(-entity_ID) %>% 
  mutate(category = 'GIFT')

rownames(gift_env_desert_df) <- gift_env_desert_df$ge_ntty
```
