---
title: "AdditionalCode_RegionalAnalysis"
author: "Johanna Klapper"
date: "7/29/2022"
output: html_document
---

Additional Code: Environmental distance and environmental drivers for regions, not checklists.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load data
```{r}
# Continent shape
continents.sf <- read_sf(here::here("data/analysis/continents/continent.shp"))

# Coarse arid raster file
arid_coarse <- raster(here::here("data/gis_data/global-ai_et0/ai_et0/arid_coarse.tif"))

# Biomes
biomes <- read_sf(here::here("data/gis_data/biomes/Ecoregions2017/Ecoregions2017.shp"))
```


# Data preparation

## Limit biomes to desert biome
```{r}
# Visualize biomes
desert_biomes <- biomes[biomes$BIOME_NUM == 13, ] %>% 
  st_make_valid()
```

## Transform aridity raster into shapefile
```{r}
# prepare aridity raster to plot with ggplot
library(stars)
arid_plot <- read_stars(here::here("./data/gis_data/global-ai_et0/ai_et0/arid_coarse.tif"))
arid_sf <- st_as_sf(arid_plot, as_points = FALSE, merge = TRUE)
```


## Divide desert areas into main regions
```{r}
desert.areas.comb <- st_join(arid_sf, desert_biomes)
plot(desert.areas.comb$geometry)

ggplot(data = continents.sf) +
  geom_sf(aes(fill = CONTINENT))

desert.areas.cont <- st_intersection(desert.areas.comb, continents.sf)

desert.areas.reg <- desert.areas.cont %>% 
  group_by(CONTINENT) %>% 
  summarise()

ggplot(desert.areas.reg) +
  geom_sf(aes(fill = CONTINENT))
```

```{r}
write_sf(desert.areas.reg, here::here("./data/analysis/desert.reg.shp")) 
```


# Species per region

## Row sums per region
```{r}
species_data_bin_cont <- merge(species, unique(polygons_data), by = "desert") %>% 
  dplyr::select(species, contnnt) %>% 
  mutate(count = 1) %>% 
  unique() %>% 
  pivot_wider(names_from=species,values_from = count,values_fill = 0,) %>% 
  as.data.frame()

rownames(species_data_bin_cont) <- species_data_bin_cont$contnnt

species_matrix_cont <- species_data_bin_cont %>% dplyr::select(-contnnt)

spec_num_cont <- rowSums(species_matrix_cont) %>% 
  as.data.frame() %>% 
  rownames_to_column() %>% 
  dplyr::rename(continent = rowname,
                spec = '.')
```


## Species per area (per region)
```{r}
ggplot(data = spec_num_cont, aes(continent, spec)) +
  geom_col()

# maybe make this as well per area?
```


```{r}
area_cont <- model_data %>% 
  group_by(continent) %>% 
  summarise(sum = sum(Area), .groups = "keep") 

area_total <- sum(model_data$Area)

area_cont$area_prop <- area_cont$sum / area_total

spec_num_cont <- merge(spec_num_cont,area_cont, by = "continent")

ggplot(data = spec_num_cont, aes(continent, spec/sum)) +
  geom_col()
```



# Environmental data for general desert areas

## Load data
```{r}
desert.reg <- read_sf(here::here("./data/analysis/desert.reg.shp"))
```



## Area
```{r}
sf::sf_use_s2(FALSE)
area_des_reg <- st_area(desert.reg) %>% 
  as.data.frame()

# sf::sf_use_s2(FALSE) -> Sonoran.shp was giving a weird error, this solved it
```


## Isolation
```{r}
# waiting for Pierre's code
```


## Annual mean temperature
```{r}
mean_temp_extract_des_reg <- exact_extract(mean_temp, desert.reg,fun=c("mean", "stdev"))
```


## Temperature seasonality
```{r}
temp_seas_extract_des_reg <- exact_extract(temp_seas, desert.reg,fun=c("mean", "stdev"))
```


## Annual mean precipitation
```{r}
mean_prec_extract_des_reg <- exact_extract(mean_prec, desert.reg,fun=c("mean", "stdev"))
```


## Precipitation seasonality
```{r}
prec_seas_extract_des_reg <- exact_extract(prec_seas, desert.reg,fun=c("mean", "stdev"))
```


## Mean altitude
```{r}
mean_alt_extract_des_reg <- exact_extract(mean_alt, desert.reg,fun=c("mean", "stdev"))
```


## Elevational range
```{r}
# Taking the single highest and single lowest point and taking the absolute difference

elev_max_max_des_reg <- exact_extract(max_alt, desert.reg,fun=c("max")) %>% 
  as.data.frame()

elev_min_min_des_reg <- exact_extract(min_alt, desert.reg,fun=c("max")) %>% 
  as.data.frame()


elev_range_des_reg <- elev_max_max_des_reg$. - elev_min_min_des_reg$. %>% 
  as.data.frame()
elev_range_des_reg <- dplyr::rename(elev_range_des_reg, Range = .)
```

## Mean TRI (terrain ruggedness index)
```{r}
mean_tri_extract_des_reg <- exact_extract(TRI, desert.reg,fun=c("mean", "stdev"))
```




## Unlist lists and create one dataframe
```{r}
desert_names_df_des_reg <- desert.reg %>% 
  dplyr::select(CONTINENT) %>% 
  st_drop_geometry()

area_df_des_reg <- area_des_reg %>% 
  dplyr::rename(Area = '.') %>% 
  units::drop_units()

mean_temp_df_des_reg <- mean_temp_extract_des_reg %>% 
  dplyr::rename(Temp = mean,
         Temp_sd = stdev)

temp_seas_df_des_reg <- temp_seas_extract_des_reg %>% 
  dplyr::rename(seasT = mean,
         seasT_sd = stdev) %>% 
  mutate(seasT = seasT/100)

mean_prec_df_des_reg <- mean_prec_extract_des_reg %>% 
  dplyr::rename(Prec = mean,
         Prec_sd = stdev)

prec_seas_df_des_reg <- prec_seas_extract_des_reg %>% 
  dplyr::rename(seasP = mean,
        seasP_sd = stdev)

mean_alt_df_des_reg <- mean_alt_extract_des_reg %>% 
  dplyr::rename(Alt = mean,
         Alt_sd = stdev)

mean_tri_df_des_reg <- mean_tri_extract_des_reg %>% 
  dplyr::rename(TRI = mean,
         TRI_sd = stdev)



# Combine dfs
environment_data_des_reg <- bind_cols(desert_names_df_des_reg, area_df_des_reg, mean_temp_df_des_reg, temp_seas_df_des_reg, mean_prec_df_des_reg, prec_seas_df_des_reg, mean_alt_df_des_reg, elev_range_des_reg, mean_tri_df_des_reg)

row.names(environment_data_des_reg) <- environment_data_des_reg$CONTINENT

environment_data_des_reg <- environment_data_des_reg %>% 
  dplyr::rename(continent = CONTINENT)
```


## Save dataset
```{r}
write.csv(environment_data_des_reg, here::here("./data/analysis/environment_data_des_reg.csv"), row.names = TRUE)
```



## Mean soil - des_reg
```{r}
mean_soil_extract_des_reg <- exact_extract(soil_1, desert.reg$geometry)

names(mean_soil_extract_des_reg) <- desert.reg$CONTINENT

soil_frac_des_reg <- lapply(mean_soil_extract_des_reg, function(x) {
  as.data.frame(x) %>% 
  group_by(value) %>% 
  dplyr::summarise(sum = sum(coverage_fraction)) %>% 
  mutate(n = sum(sum),
         frac = sum/n) %>% 
  dplyr::select(value, frac)
})

soil_frac_df_des_reg <- do.call(rbind.data.frame, soil_frac_des_reg) %>% 
  rownames_to_column()

soil_frac_df_des_reg_names <- str_remove(soil_frac_df_des_reg$rowname, pattern = "\\.\\d+$")

soil_frac_df_des_reg$continent <- soil_frac_df_des_reg_names
```

```{r}
soil_matrix <- pivot_wider(soil_frac_df_des_reg, id_cols = continent, names_from = value, values_from = frac) %>% 
  column_to_rownames(var = "continent")

soil_matrix[is.na(soil_matrix)] <- 0
```

```{r}
soil_sim <- diversity(soil_matrix, "inv")
hist(soil_sim, breaks = seq(0, 12, by = 0.2))
range(soil_sim)
```

```{r}
soil_sim_df <- soil_sim %>% 
  as.data.frame() %>% 
  rownames_to_column() %>% 
  dplyr::rename(continent = rowname,
                Soil = '.') 
```



# Inter annual precipitation
```{r}
desert.names.reg <- desert.reg %>% 
  unique() %>% 
  dplyr::select(CONTINENT) %>% 
  st_drop_geometry()


path <- c("E:/MasterThesis/prec")
setwd(path)
files.prec <- list.files(path = path, pattern = paste0(1981, "_"))
prec.raster <- sapply(files.prec, function(x) raster(x), USE.NAMES = TRUE)
prec.extract <- sapply(prec.raster, function(x) exact_extract(x, as_Spatial(desert.reg), fun = c("mean")))


prec.extract.df.reg <- prec.extract %>% 
  as.data.frame() %>% 
  mutate(mean.1981 = rowMeans(across(where(is.numeric)))) %>% 
  cbind(desert.names.reg) %>% 
  dplyr::select(CONTINENT, mean.1981)


for (i in 1982:2010) {

  path <- c("E:/MasterThesis/prec")
  setwd(path)
  files.prec <- list.files(path = path, pattern = paste0(i, "_"))
  prec.raster <- sapply(files.prec, function(x) raster(x), USE.NAMES = TRUE)
  prec.extract <- sapply(prec.raster, function(x) exact_extract(x, as_Spatial(desert.reg), fun = c("mean")))

  prec.extract <- prec.extract %>% 
    as.data.frame() %>% 
    mutate(mean = rowMeans(across(where(is.numeric)))) %>% 
    dplyr::select(mean)
  names(prec.extract) <- paste0("mean.", i)
  
  prec.extract.df.reg <- cbind(prec.extract.df.reg, prec.extract)
}

write.csv(prec.extract.df.reg, here::here("./data/analysis/prec.extract.reg.81-10.csv"), row.names = FALSE)
```

```{r}
prec.reg.sd <- prec.extract.df.reg %>%
  group_by(CONTINENT) %>% 
  mutate(interP = sd(across(where(is.numeric)))) %>% 
  dplyr::select(CONTINENT, interP) %>% 
  dplyr::rename(continent = CONTINENT)

write.csv(prec.reg.sd, here::here("./data/analysis/prec.reg.sd.81-10.csv"), row.names = FALSE)
```


```{r}
environment.data.des.reg.df <- merge(environment_data_des_reg, soil_sim_df, by = "continent") %>% 
  merge(prec.reg.sd, by = "continent")
```


## Save dataset
```{r}
write.csv(environment.data.des.reg.df, here::here("./data/analysis/environment_data_des_reg_df.csv"), row.names = FALSE)
```




# PCA - Environmental distance of regions

## Load data
```{r}
env_pred_dataset_reg <- read.csv(here::here("./data/analysis/environment_data_des_reg_df.csv"), row.names = 1)
```


## Selecting necessary columns
```{r}
env_pred_analysis_reg <- env_pred_dataset_reg %>% 
  dplyr::select(-c(seasT_sd, seasP_sd, Alt_sd, TRI_sd)) %>% 
  drop_na()
```

```{r}
ggpairs(env_pred_analysis_reg, upper = list(continuous = wrap(ggally_cor, ggally_cordigits=2)))
```

-> The distributions do not look too good, therefore I will use the log

```{r}
env_pred_analysis_log_reg <- log(env_pred_analysis_reg +1) # +1 to avoid Inf numbers
```


```{r}
pairs_reg <- ggpairs(env_pred_analysis_log_reg, upper = list(continuous = wrap(ggally_cor, digits = 2, size = 5))) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size=8),
        axis.text.y = element_text(size = 8),
        strip.text = element_text(size = 12)) 
pairs_reg

ggsave("pairsplot_reg.png", pairs_reg, device = "png", path = here::here("./data/results/"), width = 25, height = 23, units = "cm")
```


## PCA
```{r}
pca.reg <- PCA(env_pred_analysis_reg, quanti.sup = 1)
```

### Plotting preparation
```{r}
region <- read_sf(here::here("./data/analysis/desert.reg.shp"))

env_pred_dataset_na_reg <- env_pred_dataset_reg %>% 
  drop_na() %>% 
  rownames_to_column()

pca_poly_data_reg <- region %>% 
  st_drop_geometry() %>% 
  filter(CONTINENT %in% env_pred_dataset_na_reg$rowname) %>% 
  distinct(CONTINENT, .keep_all = TRUE) 
```


## Plotting with supp.var Area
```{r}
# extract pc scores for first two component and add to dataframe

pca.plot.reg <- data.frame(rep(NA, 7))
pca.plot.reg$pc1 <- pca.reg$ind$coord[, 1] # indexing the first column
pca.plot.reg$pc2 <- pca.reg$ind$coord[, 2]  # indexing the second column
pca.plot.reg$pc3 <- pca.reg$ind$coord[, 3]  # indexing the third column
pca.plot.reg$continent <- names(pca.reg$ind$dist)
pca.plot.reg <- merge(pca.plot.reg, pca_poly_data_reg, by.x = "continent", by.y = "CONTINENT")

pca.vars.sup.reg <- pca.reg$quanti.sup$coord %>% 
  data.frame
pca.vars.sup.reg <- pca.vars.sup.reg * 4
pca.vars.sup.reg$vars <- rownames(pca.vars.sup.reg)

#We also need to extract the data for the variable contributions to each of the pc axes.

pca.vars.reg <- pca.reg$var$coord %>% 
  data.frame
pca.vars.reg <- pca.vars.reg * 4
pca.vars.reg$vars <- rownames(pca.vars.reg)
pca.vars.m.reg <- melt(pca.vars.reg, id.vars = "vars")
```

```{r}
label.reg <- pca.vars.reg$vars
label.sup.reg <- pca.vars.sup.reg$vars
```

```{r}
cols.reg <- RColorBrewer::brewer.pal(8, name = "Dark2")
```

```{r}
pca.eig.reg <- pca.reg$eig[ ,2] %>% 
  as.vector() %>% 
  as.data.frame()

pca.axes.reg <- ggplot(data = pca.eig.reg, aes(x = fct_inorder(paste0("PC", 1:6), .), y = ., group = FALSE)) +
  geom_point(size = 2) +
  geom_line() +
  labs(x = "PCA axes", y = "Percentage of variance [%]") +
  theme_bw() +
  theme(rect = element_rect(size = 0.2))
```


```{r}
ggsave("pca.axes.reg.png", pca.axes.reg, device = "png", path = here::here("./data/results/"), width = 20, height = 12, units = "cm")
```



### Colored in for regions
```{r}
fig.2.reg <- ggplot() +
  geom_point(data = pca.plot.reg, aes(x = pc1, y = pc2, fill = continent, col = continent), pch = 21, size = 3.5) +
  scale_fill_manual(values = cols.reg) +
  scale_color_manual(values = cols.reg) +
  #scale_fill_brewer(palette = "Dark2", direction = 1) +
  #scale_color_brewer(palette = "Dark2", direction = 1) +
  geom_segment(data = pca.vars.reg, aes(x = 0, y = 0, xend = Dim.1, yend = Dim.2), size = 1, col = "black", arrow = arrow(length = unit(0.3,"cm"))) +
  geom_text(aes(x = Dim.1*1.2, y = Dim.2*1.2, label = label.reg), data = pca.vars.reg, check_overlap = FALSE, col = "black", size = 6) +
  geom_segment(data = pca.vars.sup.reg, aes(x = 0, y = 0, xend = Dim.1, yend = Dim.2), size = 1, col = "blue", linetype = "dashed",  arrow = arrow(length = unit(0.3,"cm"))) +
  geom_text(aes(x = Dim.1*1.2, y = Dim.2*1.2, label = label.sup.reg), data = pca.vars.sup.reg, check_overlap = TRUE, col = "blue", size = 6) +
  theme_bw() +
  theme(legend.title = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.position = c(0.15, 0.88),
        legend.box.background = element_rect(colour = "black"),
        axis.title = element_text(size = 16))+
  labs(x = "PC 1 (-.-%)", y = "PC 2 (-.-%)", fill = "Region", col = "Region")+
  guides(fill=guide_legend(ncol=2, keywidth = 0.6, keyheight = 0.6)) +
  xlim(-6, 5)
fig.2.reg

#fig.2.reg <- ggMarginal(fig.2a.reg, groupFill = TRUE, groupColour = TRUE)
ggsave("figure2.reg.png", fig.2.reg, device = "png", path = here::here("./data/results/"), width = 29, height = 18, units = "cm")
```



# Model - per region
```{r}
Asia <- model_data_log_main %>% 
  filter(continent == "Asia")

glm.asia <- glm.nb(spec ~ Area + Range + seasT + Temp + Prec + seasP + Alt + TRI + Soil + Temp_sd + Prec_sd, data = Asia)
summary(glm.asia)
```

```{r}
North_Africa <- model_data_log_main %>% 
  filter(continent == "North Africa")

glm.naf <- glm.nb(spec ~ Area + Range + seasT + Temp + Prec + seasP + Alt + TRI + Soil + Temp_sd + Prec_sd, data = North_Africa)
summary(glm.naf)
```

```{r}
North_America <- model_data_log_main %>% 
  filter(continent == "North America")

glm.na <- glm.nb(spec_ ~ Area + Range + seasT + Temp + Prec + seasP + Alt + TRI + Soil + Temp_sd + Prec_sd, data = North_America)
summary(glm.na)
```

```{r}
South_Africa <- model_data_log_main %>% 
  filter(continent == "South Africa")

glm.saf <- glm.nb(spec ~ Area + Range + seasT + Temp + Prec + seasP + Alt + TRI + Soil + Temp_sd + Prec_sd, data = South_Africa)
summary(glm.saf)
```

```{r}
South_America <- model_data_log_main %>% 
  filter(continent == "South America")

glm.sa <- glm(spec ~ Area + Range + seasT + Temp + Prec + seasP + Alt + TRI + Soil + Temp_sd + Prec_sd, data = South_America)
summary(glm.sa)
```

```{r}
Oceania <- model_data_log_main %>% 
  filter(continent == "Oceania")

glm.oc <- glm(spec ~ Area + Range + seasT + Temp + Prec + seasP + Alt + TRI + Soil + Temp_sd + Prec_sd, data = Oceania)
summary(glm.oc)
```
